---
title: "Package compilation and basic run - current version 3.4"
author: "Emmanuelle Comets"
date: "15/06/2023"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(roxygen2)
# Where to find the development files of npde (folders npde/R, keep, data)
workDir<-"/home/eco/work/npde/npde30"

# Compilation directory
compilDir<-"/home/eco/work/npde/compileNpde"

knitr::opts_chunk$set(root.dir = workDir)
```

## Compilation

First creation date: **02/02/2021**

- structure
  - **tests** : removed all other folders and files except testthat from the package otherwise warnings about RDS files
  - **data** : removed remifentanil example from data folder
- **roxygen** documentation
  - warnings for ggplot (no visible global function definition)
  - added import command for pnorm (found in distribution plot) and median (found nowhere, so suspect it's the name median used in the ggplot plots, but added it all the same)
- **package size**: still 5.9 Mb so much too large for CRAN 
  - the 3 simulated data files for warfarin and viral load data are all around 5Mb, consider making them available only on bookdown/website
- necessary files
  - added a DESCRIPTION file
  - added a CHANGES file
- for compilation: 
  - removed NAMESPACE
  - removed man pages
- Compilation steps from Build menu
  - Document => create NAMESPACE, DESCRIPTION (update collate directive), create man pages
  - Check => update documentation, create NAMESPACE
- **FINAL COMPILATION FOR CRAN**
  - removed documentation (too large)
  - removed simwarfarineBase 
  - still over 5Mo but seems to be ok
- CRAN pre-test doesn't pass :-/
  - added importFrom for ggplot functions, also for gridExtra (grid.arrange) and grid
  - 'solved' problem by adding a dependency on rlang
    - partially fixed with rlang
    - workaround by defining global variables so check won't complain about them, but we need to use the .data systematically in ggplot aes() => **Romain TODO**
- **March 2021**
  - mail Fu (15/03): added again the option to save the output in autonpde (probably removed by Romain :-/ )
- **June 2023**
  - fixed scatterplot when only one X-value (removed interpolation in this case as was causing the plot to fail)
  - note: the case when this happens within covsplit is **not fixed**

```{r compilation}
# Reduce size of viral load simulation data (to 500 simulations) for CRAN
if(FALSE) {
  cmd<-paste("mv ", file.path(workDir,"npde","data","simvirload.tab")," ", file.path(workDir,"keep","data","/"),sep="")
  system(cmd)
  tab<-read.table(file.path(workDir,"npde","data","simvirload.tab"), header=TRUE)
  tab1<-tab[1:(dim(tab)[1]/2),]
  write.table(tab1, file.path(workDir,"npde","data","simvirload.tab"), quote=FALSE, row.names=FALSE, col.names=TRUE)
}

cmd<-paste("rm -r ",file.path(compilDir,"*"),sep="")
system(cmd)
dir.create(compilDir)
dir.create(file.path(compilDir,"npde"))
dir.create(file.path(compilDir,"npde","inst"))
# File too large
if(FALSE) {
  cmd<-paste("cp ", file.path(workDir,"latexDoc","userguide_3_3.pdf")," ", file.path(compilDir,"inst","userguide_npde_3.4.pdf"),sep="")
  system(cmd)
}

cmd<-paste("cp -rp ",file.path(workDir,"npde","R")," ", file.path(compilDir,"npde"),sep="")
system(cmd)
cmd<-paste("cp -rp ",file.path(workDir,"data")," ", file.path(compilDir,"npde"),sep="")
system(cmd)
for(ifile in c("CHANGES","DESCRIPTION")) {
  cmd<-paste("cp ",file.path(workDir,"keep",ifile)," ", file.path(compilDir,"npde"),sep="")
  system(cmd)
}
for(ifile in c("CITATION")) {
  cmd<-paste("cp ",file.path(workDir,"keep",ifile)," ", file.path(compilDir,"npde","inst"),sep="")
  system(cmd)
}
# cmd<-paste("cp ",file.path(workDir,"LICENSE")," ", file.path(compilDir,"inst"),sep="")
# system(cmd)

```

```{r document,echo=FALSE,message=FALSE,warnings=FALSE, results=FALSE}
# Compile
setwd(file.path(compilDir,"npde"))
devtools::document()
setwd(file.path(compilDir,"npde"))
roxygenise()
```

```{r building}
setwd(compilDir)
system("R CMD build npde")
system("R CMD check --as-cran --run-donttest npde_3.4.tar.gz")
```

#### npde 3.1

Apres correction, la compilation du package passe sans erreurs et avec 2 notes restantes.

- **notes**
  - previous version archived
  - package size too large (recommended size less than 5Mb): reduce nb of simulations for warfarin ?
  - ggplot variables (rien a faire pour ça)
- **warnings** corriges
  - jeux de donnees non documentes: removed remifentanil, added virload documentation (used to be a specific man page, reintegrated them into roxygen format in npde.R like warfarin)
  - duplicated alias: fixed !

#### npde 3.2, 3.3

- **notes**
  - time to run examples
Examples with CPU or elapsed time > 5s
                 user system elapsed
npde.cens.method 7.51  0.019   7.605

### Warnings

- ggplot warnings
  - solved in npde 3.0 by adding global variables (horrible)
    - in 3.3, tried to add .data$ to all the ggplot functions
  - can't remove the .x because of scales

````
Undefined global functions or variables:
  .x X2.5. X50. X97.5. Y0.025 Y0.025.1 Y0.5 Y0.5.1 Y0.975 Y0.975.1 aes
  annotation_logticks category coord_cartesian coord_flip element_blank
  element_line element_rect element_text expand_limits facet_wrap
  geom_bar geom_boxplot geom_crossbar geom_hline geom_line geom_point
  geom_ribbon ggplot ggtitle gpar grid.arrange group grp guides labs
  lower name obs.inf obs.median obs.sup pinf.lower pinf.median
  pinf.upper pmid.lower pmid.median pmid.upper psup.lower psup.median
  psup.upper scale_fill_manual scale_x_continuous scale_x_discrete
  scale_x_log10 scale_y_continuous scale_y_log10 textGrob theme upper
  value x x1 x2 x_area_0.25 x_area_0.5 x_area_0.975 xcent y y1 y2
  y_area_0.25 y_area_0.5 y_area_0.975
````
- Warnings in first compilation (solved)

````
  checking Rd metadata ...
   Rd files with duplicated alias 'aux.npdeplot.computepi':
     ‘npde.plot.default.Rd’ ‘npde.plot.scatterplot.Rd’
   Rd files with duplicated alias 'compute.bands':
     ‘npde.plot.default.Rd’ ‘npde.plot.scatterplot.Rd’
   Rd files with duplicated alias 'compute.bands.true':
     ‘npde.plot.default.Rd’ ‘npde.plot.scatterplot.Rd’
   Rd files with duplicated alias 'npde':
     ‘npde-package.Rd’ ‘npde.Rd’
W  checking for missing documentation entries (346ms)
   Undocumented code objects:
     ‘remifent’ ‘simremifent’ ‘simremifent_base’ ‘simvirload’ ‘virload’
     ‘virload20’ ‘virload50’ ‘virloadMDV20’
   Undocumented data sets:
     ‘remifent’ ‘simremifent’ ‘simremifent_base’ ‘simvirload’ ‘virload’
     ‘virload20’ ‘virload50’ ‘virloadMDV20’
   All user-level objects in a package should have documentation entries.
   See chapter ‘Writing R documentation files’ in the ‘Writing R
   Extensions’ manual.
````

### Install package in development mode
  
```{r devModeInstall}
dev_mode() # development mode
install.packages(pkgs=file.path(compilDir,"npde_3.4.tar.gz"),repos=NULL)
library(npde)
library(ggplot2)
library(gridExtra)
library(mclust)
library(testthat)
library(grid)
```

# Theophylline

- computation of npde and npd
- default plots

```{r theo, echo=FALSE}
data(theopp)
data(simtheopp)

# Calling autonpde with dataframes
x<-autonpde(theopp,simtheopp,1,3,4,boolsave=FALSE)
plot(x)
head(x["results"]["res"])

plot(x, plot.type="hist")
```

# Warfarin

- covariate plots
- reference profiles

```{r runNpdeWarf, echo=FALSE}
data(warfarin)
data(simwarfarinCov)
# Warfarin data, using files on disk
wcov<-autonpde(namobs=warfarin,namsim=simwarfarinCov, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfCov", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")), boolsave=FALSE)

plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov=c("wt", "sex"))
plot(wcov, plot.type="ecdf", covsplit=TRUE, which.cov=c("wt", "sex"))


plot.tnpde<-plot(wcov, plot.type="x.scatter", ref.prof=list(id=2), main="tnpd with reference profile ID=2")
plot.vpc<-plot(wcov, plot.type="vpc", main="VPC")
grid.arrange(grobs=list(plot.tnpde, plot.vpc), nrow=1, ncol=2)

```
# Viral load, base plots


```{r baseplot, echo=FALSE}
#Viral load data
data(virload20)
data(simvirload)

yvir20<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE)
yvir20.omit<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE, cens.method="omit")

plot(yvir20)
plot(yvir20, plot.type="loq")
plot(yvir20, plot.type="vpc")
plot(yvir20, plot.type="x.scatter")
```


```{r grid.arrange, echo=FALSE}
plot.x.scatter.yvir20 = plot(yvir20,plot.type="x.scatter")
plot.pred.scatter.yvir20 = plot(yvir20,plot.type="pred.scatter")
grid.arrange(grobs=list(plot.x.scatter.yvir20, plot.pred.scatter.yvir20), nrow=1, ncol=2)

plot.vpc.yvir20 = plot(yvir20,plot.type="vpc")
plot.yvir20.omit = plot(yvir20.omit,plot.type="vpc")
grid.arrange(grobs=list(plot.vpc.yvir20,plot.yvir20.omit), nrow=1, ncol=2)

```


## End of file, deactivating development mode

```{r deactivateDevMode, echo=FALSE, hide=T}
dev_mode()
```

### Bugs to sort

### Sort out covariate plots

There were two functions with almost the same name
- npde.plot.covariates: regular plots split by covariates, only for x, pred, ecdf => renamed to **npde.plot.splitcov** and added options hist and qqplot
  - do we need those subplots, or maybe just simplify call to function (use covsplit and capture arguments instead of using which.plot)
- npde.plot.covariate: covariate plots as in Brendel => kept as is

#### plot.NpdeRes (dans plotNpde-methods.R)

- **Romain TODO**: la fonction devrait prendre un objet NpdeRes et pas un objet NpdeObject (NpdeRes n'a pas d'element data, c'est juste le slot res d'un element NpdeObject !!!)
  - il faut lui donner des defauts pour xlab, ylab (et la possiblite de passer outre en passant des arguments en ...)
  - normalement il doit y avoir l'equivalent de xobs dans le dataframe res de l'objet
  - pas sure qu'on ait not.miss mais dans ce cas le reconstruire (a tester +++)
  - il n'y a pas de liste plot.opt donc prendre des defauts dans set.default.options()
- faire un testthat pour verifier que cette fonction marche par elle-meme  (use testthat for class to generate an object npdeData and plot it)

#### plot.NpdeData (dans plotNpde-methods.R)

- **Romain TODO**: faire un testthat pour veeifier que la fonction et les options passent (use testthat for class to generate an object npdeData and plot it)

