---
title: "Code merge - Distribution plots"
author: "Emmanuelle Comets"
date: "22/01/2021"
output:
  pdf_document: default
  html_document: default
---

## Summary

### Objective

Recode **aux.plot.hist** and **aux.plot.dist** to simplify their structure.

### Current issue

Sorting the covariates in the facet plot

### Requirements

- main function  **npde.plot.dist()**
  - input: npdeObject, which (variable to plot), dist.type (plot type, one of hist, qqplot, ecdf), "..."
  - output: one plot
- auxiliary functions **aux.npdeplot.hist()** and  **aux.npdeplot.dist()**
  - input: both functions should take as input
    - a dataframe obsmat: matrix with the data to plot, with columns
      - x; variable to plot
      - category: covariate category (if "all", overall plot)
    - graphical options: plot.opt
    - distrib: reference distribution plot (one of norm, unif)
    - sim.ypl:  if given, a vector of simulated data for the variable to plot
    - for aux.npdeplot.hist(), nclass (nb of classes)
  - output
    - distribution plots: histogram (aux.plot.hist), ecdf or qqplot (aux.plot.dist)
    - note: QQ-plot for uniform variable is similar to ecdf (theoretical quantiles correspond to the cumulative density function)

### Defining folders, loading libraries

```{r setup, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(grid)
library(mclust)
library(testthat)
#workDir<-"D:/RECHERCHES/_NPDE/Npde-2021/npde30-main"
workDir<-"/home/eco/work/npde/npde30"
notesDir<-file.path(workDir,"notebooks")
datDir<-file.path(workDir,"data")
fullDatDir<-file.path(workDir,"keep","data") # Full data files (some removed from package to decrease size on CRAN)
testsDir<-file.path(workDir,"tests","testthat")
setwd(workDir)
```

### Loading functions

```{r setupOldPackage, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Classes from the package
source(file.path(workDir,"npde","R","aaa_generics.R"))
source(file.path(workDir,"npde","R","npdeControl.R"))
source(file.path(workDir,"npde","R","NpdeData.R"))
source(file.path(workDir,"npde","R","NpdeSimData.R"))
source(file.path(workDir,"npde","R","NpdeData-methods.R"))
source(file.path(workDir,"npde","R","NpdeRes.R"))
source(file.path(workDir,"npde","R","NpdeRes-methods.R"))
source(file.path(workDir,"npde","R","NpdeObject.R"))
source(file.path(workDir,"npde","R","NpdeObject-methods.R"))

# Computational functions from the package
source(file.path(workDir,"npde","R","compute_distribution.R"))
source(file.path(workDir,"npde","R","compute_npde.R"))
source(file.path(workDir,"npde","R","compute_pd.R"))
source(file.path(workDir,"npde","R","compute_ploq.R"))
source(file.path(workDir,"npde","R","mainNpde.R"))
source(file.path(workDir,"npde","R","npde.R"))

# Plot functions from the package - kept, some changes
source(file.path(workDir,"npde","R","plotNpde-methods.R"))
source(file.path(workDir,"npde","R","plotNpde-plotFunctions.R"))
source(file.path(workDir,"npde","R","plotNpde-binningPI.R")) # renamed from plotNpde-unitFunctionsPI.R

# Scatterplots
source(file.path(workDir,"npde","R","plotNpde-auxScatter.R")) # replaces plotNpde-unitFunctionsRef.R
source(file.path(workDir,"npde","R","plotNpde-auxScatterPlot.R"))
source(file.path(workDir,"npde","R","plotNpde-scatterplot.R")) # replaces plotNpde-meanProf.R

# Distribution plots
source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
source(file.path(workDir,"npde","R","plotNpde-distributionPlot.R")) # extracted "main" for distribution plots from plotNpde-plotFunctions.R
  source(file.path(workDir,"npde","R","plotNpde-covplot.R"))
```

### Run npde

```{r runNpde, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Warfarin data, using files on disk
wbase<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(fullDatDir, "simwarfarinBase.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

wcov<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(fullDatDir, "simwarfarinCov.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))
```

### Prepare objects 

```{r prepareObsmat, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# no covariate
obs.nocov<-wbase@results@res[,"npde",drop=FALSE]
obs.nocov$category<-factor("all")
colnames(obs.nocov)[1]<-"x"

# Covariates
npdeObject<-wbase
idobs <- npdeObject["data"]["data"][npdeObject["data"]["not.miss"], npdeObject["data"]["name.group"]]
plot.opt<-npdeObject["prefs"]

## covariate sex
obs.sex<-data.frame(x=wbase@results@res[,"npde"], category=paste("sex:", wbase@data@data$sex))
obs.sex$category <- factor(obs.sex$category)

## covariate weight
zecov<-wbase@data@data$wt
lcov<-"Weight:"
ucov = zecov[match(unique(idobs),idobs)]
if(is.numeric(ucov) & length(unique(ucov))>plot.opt$ncat){ # Continuous covariatewith more than plot.opt$ncat (default 3)
  if(plot.opt$ncat!=3) { # 3 categories or less
    ncat<-plot.opt$ncat
    seqcat<-seq(0,1,length.out=(ncat+1))
    zecov.cat<-cut(zecov,breaks=quantile(ucov,seqcat), include.lowest=TRUE, ordered_result=TRUE)
    nam1<-paste("q",format(seqcat[-(ncat+1)],digits=2),"-q",format(seqcat[-1],digits=2),sep="")
    namcat<-paste(namcov,nam1,sep=": ")
    zecov.cat<-factor(zecov.cat, labels=namcat)
  } else { # if more than 3 categories, split in 3 ranges
    zecov.cat<-cut(zecov,breaks=quantile(ucov,c(0,0.25,0.75,1)), include.lowest=TRUE, ordered_result=TRUE)
    namcat<-paste(lcov,c("<Q1","Q1-Q3",">Q3"),sep=": ")
    zecov.cat<-factor(zecov.cat, labels=namcat)
  }
} else { # Categorical covariate defined as factor, or covariate with less than plot.opt$ncat categories
  namcat<-paste(lcov,unique(ucov), sep=": ")
  zecov.cat<-paste(lcov, zecov, sep=": ")
  zecov.cat<-factor(zecov.cat, labels=namcat)
}

obs.weight<-data.frame(x=wbase@results@res[,"npde"], category=zecov.cat)

# with pd
obspd.sex<-obs.sex
obspd.sex$x<-wbase@results@res[,"pd"]
```

## Debug auxiliary plots

### Histogram

- 3 plots: no covariate, sex in 2 categories, weight in 3 categories
- problem with sorting the categories 

```{r debugHist, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
distrib<-"norm"
nclass<-10
plot.opt2<-npdeObject@prefs
plot.opt2$main<-""
plot.opt2$xlab <- "npde"
plot.opt2$ylab <- "Counts"
plot.opt2$alpha <- 0.5
aux.npdeplot.hist(obs.nocov, plot.opt2)

plot.opt2$which.cov<-"sex"
aux.npdeplot.hist(obs.sex, plot.opt2)

plot.opt2$which.cov<-"wt"
plot.opt2$main<-"Histogram of npde by weight category"
aux.npdeplot.hist(obs.weight, plot.opt2)

```

### Distribution plot:  ecdf

```{r debugEcdf, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Addding censoring column
obs.nocov$cens<-0
obs.sex$cens<-0
obs.weight$cens<-0
obspd.sex$cens<-0

source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
distrib<-"norm"
plot.opt2<-npdeObject@prefs
plot.opt2$main<-"Plot ecdf"
plot.opt2$ylab <- "npde"
plot.opt2$xlab <- "Empirical cumulative density function"
aux.npdeplot.dist(obs.nocov, plot.opt2, dist.type="ecdf")

plot.opt2$which.cov<-"sex"
plot.opt2$main<-""
aux.npdeplot.dist(obs.sex, plot.opt2, dist.type="ecdf")

plot.opt2$which.cov<-"wt"
plot.opt2$main<-"ecdf of npde by weight category"
aux.npdeplot.dist(obs.weight, plot.opt2, dist.type="ecdf")

# pd
plot.opt2$main<-"Plot ecdf"
plot.opt2$ylab <- "pd"
plot.opt2$xlab <- "Empirical cumulative density function"
aux.npdeplot.dist(obspd.sex, plot.opt2, distrib="unif", dist.type="ecdf")

```

### Distribution plot: qqplot

```{r debugQQplot, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
distrib<-"norm"
plot.opt2<-npdeObject@prefs
plot.opt2$main<-""
plot.opt2$xlab <- "Theoretical nnpde"
plot.opt2$ylab <- "Empircal npde"
aux.npdeplot.dist(obs.nocov, plot.opt2)

aux.npdeplot.dist(obs.sex, plot.opt2)

plot.opt2$which.cov<-"wt"
plot.opt2$main<-"Histogram of npde by weight category"
aux.npdeplot.dist(obs.weight, plot.opt2)
```

## Debug main distribution plot function


```{r debugMainDistplot}
source(file.path(workDir,"npde","R","plotNpde-distributionPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
npde.plot.dist(wbase,  which="npde", dist.type="qqplot")

npde.plot.dist(wbase,  which="npde", dist.type="qqplot", covsplit=TRUE, which.cov=c("wt"))
npde.plot.dist(wbase,  which="npde", dist.type="qqplot", covsplit=TRUE, which.cov=c("sex"))
npde.plot.dist(wbase,  which="npde", dist.type="qqplot", covsplit=TRUE, which.cov=c("all"))

npde.plot.dist(wbase,  which="npde", dist.type="ecdf", covsplit=TRUE, which.cov=c("age"))
npde.plot.dist(wbase,  which="npde", dist.type="hist", covsplit=TRUE, which.cov=c("sex"))

# debut
if(FALSE) {
  npdeObj<-wbase
  plot.opt<-npdeObject@prefs
  which<-"npde"
  plot.opt$covsplit<-TRUE
  plot.opt$which.cov<-c("wt")
  dist.type="ecdf"
}
```

