---
title: "Code integration"
author: "Emmanuelle Comets"
date: "21/01/2021"
output:
  pdf_document: default
  html_document: default
---

### Objective

Set up a debugging framework:
- load libraries
- load package functions individually
- prepare objects for debugging functions

### Defining folders, loading libraries

```{r setup, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(grid)
library(mclust)
library(testthat)
workDir<-"/home/eco/work/npde/npde30"
knitr::opts_chunk$set(root.dir = workDir)
notesDir<-file.path(workDir,"notebooks")
datDir<-file.path(workDir,"npde","data")
fulldatDir<-file.path(workDir,"keep","data")
testsDir<-file.path(workDir,"npde","tests","testthat")
setwd(workDir)
```

### Creating NpdeObject using the current version of the package

```{r setupOldPackage, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Classes from the package
source(file.path(workDir,"npde","R","aaa_generics.R"))
source(file.path(workDir,"npde","R","npdeControl.R"))
source(file.path(workDir,"npde","R","NpdeData.R"))
source(file.path(workDir,"npde","R","NpdeSimData.R"))
source(file.path(workDir,"npde","R","NpdeData-methods.R"))
source(file.path(workDir,"npde","R","NpdeRes.R"))
source(file.path(workDir,"npde","R","NpdeRes-methods.R"))
source(file.path(workDir,"npde","R","NpdeObject.R"))
source(file.path(workDir,"npde","R","NpdeObject-methods.R"))

# Computational functions from the package
source(file.path(workDir,"npde","R","compute_distribution.R"))
source(file.path(workDir,"npde","R","compute_npde.R"))
source(file.path(workDir,"npde","R","compute_pd.R"))
source(file.path(workDir,"npde","R","compute_ploq.R"))
source(file.path(workDir,"npde","R","mainNpde.R"))
source(file.path(workDir,"npde","R","npde.R"))

# Plot functions from the package - kept, some changes
source(file.path(workDir,"npde","R","plotNpde-methods.R"))
source(file.path(workDir,"npde","R","plotNpde-plotFunctions.R"))
source(file.path(workDir,"npde","R","plotNpde-auxScatter.R")) 
source(file.path(workDir,"npde","R","plotNpde-auxScatterPlot.R")) 
source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
source(file.path(workDir,"npde","R","plotNpde-distributionPlot.R")) # extracted "main" for distribution plots from plotNpde-plotFunctions.R
source(file.path(workDir,"npde","R","plotNpde-scatterplot.R")) # extracted "main" for scatter plots f
source(file.path(workDir,"npde","R","plotNpde-binningPI.R")) # renamed from plotNpde-unitFunctionsPI.R
source(file.path(workDir,"npde","R","plotNpde-covplot.R")) # covariate plots as boxplots
```

### Run npde

- theophylline
- viral load (different)
- warfarin (2 models, covariates)

```{r runNpdeTheo, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}

theofit1<-autonpde(file.path(datDir, "theopp.tab"),namsim=file.path(datDir, "simtheopp.tab"),1,3,4,boolsave=FALSE, units=list(x="hr",y="mg/L"))

# Warfarin data, using files on disk
wbase<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(fulldatDir, "simwarfarinBase.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

wcov<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(fulldatDir, "simwarfarinCov.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

# Warfarin with MDV
warfmdv<-read.table(file.path(datDir, "warfarin.tab"), header=TRUE)
idx<-sample(1:dim(warfmdv)[1], 10)
warfmdv$mdv<-0
warfmdv$mdv[idx]<-1
expect_equal(sum(warfmdv$mdv),10)

wmdv<-autonpde(namobs=warfmdv,namsim=file.path(fulldatDir, "simwarfarinCov.tab"), iid=1,ix=2,iy=4,imdv=9,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

```

```{r runNpdeVIH, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
virload<-read.table(file.path(datDir, "virload.tab"), header=TRUE)
virload20<-read.table(file.path(datDir, "virload20.tab"), header=TRUE)
virload50<-read.table(file.path(datDir, "virload50.tab"), header=TRUE)
simvirload<-read.table(file.path(fulldatDir, "simvirload.tab"), header=TRUE)

yvir1<-autonpde(virload,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))

yvir20<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE)

yvir2<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE)

yvir50<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE)

# Different methods to handle LOQ
yvir50.omit<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="omit")

yvir50.ppred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="ppred")

yvir50.ipred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4, iipred=5, boolsave=FALSE, cens.method="ipred")

# noms ds ecoDocPlots.Rmd
xvir<-yvir1
x20<-yvir20
x50<-yvir50
x50.ipred<-yvir50.ipred
x50.omit<-yvir50.omit
x50.ppred<-yvir50.ppred
```

### Debugging 


```{r yloq, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
plot(yvir20)

plot(yvir20, plot.type="x.scatter")

plot(yvir20, plot.type="pred.scatter")

plot(yvir20, plot.type="hist")

plot(yvir20, plot.type="qqplot")

plot(yvir20, plot.type="vpc")

plot(yvir20, plot.type="loq")

hist20<-plot(yvir20, plot.type="hist")
xscatter20<-plot(yvir20, plot.type="x.scatter")
predscatter20<-plot(yvir20, plot.type="pred.scatter")
qqplot20<-plot(yvir20, plot.type="qqplot")
list_plot<-list(hist20, qqplot20, xscatter20, predscatter20)

grid.arrange(grobs = list_plot,nrow=2, ncol=2,vjust = 1, gp = gpar(fontsize=yvir20@prefs$size.main))

```

#### dispatching function

```{r troispetitspoints, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}

test_file(file.path(testsDir,"test-arguments-ellipsis.R"))

test_file(file.path(testsDir,"test-modifyOptions.R"))


```

#### covariate plots

```{r covariate, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
npde.plot.scatterplot(wcov, which.x="cov", which.y="npd", which.cov="wt")

npdeObject<-wcov
plot.opt<-wcov@prefs
which.x<-"cov"
which.y<-"npd"
plot.opt$which.cov<-"wt"
ref.prof<-NULL

```

#### distribution plots

```{r debugSetup, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
npde.plot.dist(yvir50.omit)
npde.plot.dist(yvir50.omit, dist.type="ecdf")
npdeObject<-yvir50.omit
which<-"npde"
plot.opt<-yvir50.omit@prefs

npde.plot.scatterplot(yvir50.omit)
npdeObject<-yvir50.omit
plot.opt<-yvir50.omit@prefs
which.x<-"x"
which.y<-which
ref.prof<-NULL

npde.plot.scatterplot(yvir50.omit)
plot(yvir50.omit, plot.type="x.scatter")

```

### Arguments to plot function

```{r debugArgs, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}

plot.NpdeObject2 <- function(x, y, ...) {
  
  args1<-match.call(expand.dots=TRUE)
  list.args <- list(...)
  list.args<-list.args[!(names(list.args) %in% c("dist.type", "which.x", "which.y", "which"))]
  force.new<-"new"
  list.args$npdeObject <- x
  list.plot.qqplot = list()
  list.args$dist.type<-"qqplot"
  list.args$new <- force.new
  typmet<-"npde"
  for(imet in typmet) {
    list.args$which <- typmet
    list.plot.qqplot[[imet]] <-do.call(npde.plot.dist, list.args)
  }
  if(length(typmet)==1) list.plot.qqplot<-list.plot.qqplot[[1]]
  return(list.plot.qqplot)
}

x<-plot.NpdeObject2(theofit1, dist.type="qqplot")


```
