---
output:
  pdf_document: default
  html_document: default
---
---
title: "Generating plots in the documentation (section Examples)"
author: "Emmanuelle Comets"
date: "02/02/2021"
output:
  pdf_document: default
  html_document: default
---


## Objective

Generate the plots for the LaTeX user guide

## Setup

### loading libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(mclust)
library(testthat)
library(grid) # grid.arrange
library(Cairo)
workDir<-"/home/eco/work/npde/npde30"
fullDatDir<-file.path(workDir,"keep","data") # Full data files (some removed from package to decrease size on CRAN)
knitr::opts_chunk$set(root.dir = workDir)
docFigs<-file.path(workDir,"latexDoc","figsDev")
saveDocPlots<-TRUE
```

### Install package in development mode
  
```{r devModeInstall}
dev_mode() # development mode
install.packages(pkgs=file.path(workDir,"npde_3.0.tar.gz"),repos=NULL)
library(npde)
```

### Run examples

- remove warnings (name.ipred empty, etc...)  **Romain** fait

```{r theoRun, echo=FALSE}
# Calling autonpde with dataframes
data(theopp)
data(simtheopp)
theofit<-autonpde(theopp,simtheopp,1,3,4,boolsave=FALSE, units=list(x="hr",y="mg/L"))

# Viral load
data(virload)
data(virload20)
data(virload50)
data(simvirload)

# full data
if(FALSE) xvir<-autonpde(virload,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))
# cdf method
if(FALSE) x20<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))
x50<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))

# Different methods to handle LOQ
x50.omit<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="omit", units=list(x="hr", y="cp/mL, log 10 base"))
x50.ppred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="ppred", units=list(x="hr", y="cp/mL, log 10 base"))
x50.ipred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4, iipred=5, boolsave=FALSE, cens.method="ipred", units=list(x="hr", y="cp/mL, log 10 base"))

# Warfarine
data(warfarin)
data(simwarfarinCov)
simbase<-read.table(file.path(fullDatDir, "simwarfarinBase.tab"), header=TRUE)

wbase<-autonpde(namobs=warfarin,namsim=simbase, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="mg/L", covariates=c("mg","kg","-","yr")))

wcov<-autonpde(namobs=warfarin,namsim=simwarfarinCov, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfCov", units=list(x="hr",y="mg/L", covariates=c("mg","kg","-","yr")))

```

## Theophylline example

- data
  - le plot(npdeData) ne marche pas **Romain** à faire pour la 3.1 (si possible en essayant d'utiliser le même code de base)
  - pour faire un graphe il faut passer par *plot.type="data"* ou *npde.plot.data()*
- VPC, scatterplot  **Eco fait**
  - modifié pour que le tracé des percentiles observés soit fait avec les linetype et size de lobs (pas des bandes), par contre la couleur matche celle de la bande de prédiction correspondante

```{r docTheo, echo=FALSE}

plot(theofit@data) # ne marche pas

# Raw data
namfile<-file.path(docFigs,"doc_theodata_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
#  plot(theofit@data, plot.loq=FALSE, size.pobs=2)
plot(theofit, plot.type="data")
# plot(theofit, plot.type="data", size.pobs=2, xlab="Time (hr)",ylab="Theophylline concentrations (mg/L)")
if(saveDocPlots) dev.off()

# Default waffle plot
namfile<-file.path(docFigs,"doc_theodefault_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(theofit)
if(saveDocPlots) dev.off()

# VPC
namfile<-file.path(docFigs,"doc_theovpc_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(theofit, plot.type="vpc")
if(saveDocPlots) dev.off()

```

## Viral load example

- data
  - mêmes problèmes que plus haut
  - LOQ data should be plotted  **Romain**
  - besoin de faire un waffle plot avec les 4 objets data, **Romain TODO** possible ? (sinon sauver 4 graphes)
  - complete data according to the censoring method when an npdeObject is given (plot just the LOQ data when the plot is called directly on a npdeData object) **Romain**

```{r docVirloadData, echo=FALSE}
# p1<-npde.plot.data(x50, plot.default=TRUE) # non, c'est pas ça
# Raw data
namfile<-file.path(docFigs,"doc_data50_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
x1<-plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", line.loq=TRUE, ylim=c(0,6.5), main="LOQ imupted using cdf")
x2<-plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", plot.loq=FALSE, line.loq=TRUE, ylim=c(0,6.5), main="LOQ removed from plot")
x3<-plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", impute.loq=FALSE, line.loq=TRUE, ylim=c(0,6.5), main="LOQ as in dataset before imputation")
x4<-plot(x50.ipred, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", line.loq=TRUE, ylim=c(0,6.5), main="LOQ imputed to individual prediction")
grid.arrange(grobs=list(x1,x2,x3,x4), nrow=2, ncol=2)
if(saveDocPlots) dev.off()

if(FALSE) {
  x1<-plot(x, plot.type="hist")
  x2<-plot(x, plot.type="qqplot")
  x3<-plot(x, plot.type="x.scatter")
  x4<-plot(x, plot.type="pred.scatter")
  grid.arrange(grobs=list(x1,x2,x3,x4), nrow=2, ncol=2)
}
    
```

- scatterplots and VPC
  - pb with VPC of x50  **Eco fait**
- possibilité d'utiliser un grid.arrange pour les 2 derniers graphes  ?  **Romain**
- VPC missing tite on y-axis
  
```{r docVirload, echo=FALSE}
# Diagnostics plots, cdf method (default)
namfile<-file.path(docFigs,"x50_cdf_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50)
if(saveDocPlots) dev.off()
# Diagnostics plots, omit method
namfile<-file.path(docFigs,"x50_omit_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.omit)
if(saveDocPlots) dev.off()
# Diagnostics plots, ipred method
namfile<-file.path(docFigs,"x50_ipred_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.ipred)
if(saveDocPlots) dev.off()
# Diagnostics plots, ppred method
namfile<-file.path(docFigs,"x50_ppred_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.ppred)
if(saveDocPlots) dev.off()
# VPC
namfile<-file.path(docFigs,"doc_vpc50_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50,plot.type="vpc", line.loq=TRUE)
plot(x50.omit,plot.type="vpc")
if(saveDocPlots) dev.off()

# Scatterplot
namfile<-file.path(docFigs,"virload_xscatter_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.omit,plot.type="x.scatter")
plot(x50,plot.type="x.scatter")
if(saveDocPlots) dev.off()

# User-defined waffle plots
vpc.omit<-plot(x50.omit,plot.type="vpc")
vpc.cdf<-plot(x50,plot.type="vpc")

namfile<-file.path(docFigs,"userwaffle_vpc.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
grid.arrange(grobs=list(vpc.omit, vpc.cdf), nrow=1, ncol=2)
if(saveDocPlots) dev.off()

xscatter.omit<-plot(x50.omit,plot.type="x.scatter")
xscatter.cdf<-plot(x50,plot.type="x.scatter")

namfile<-file.path(docFigs,"userwaffle_xscatter.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
grid.arrange(grobs=list(xscatter.omit, xscatter.cdf), nrow=1, ncol=2)
if(saveDocPlots) dev.off()

```

- P(Y<LOQ): changed defaults

```{r docVirloadLOQ, echo=FALSE}

# P(Y<LOQ)
namfile<-file.path(docFigs,"virload_ploq_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50,plot.type="loq", main=" ")
if(saveDocPlots) dev.off()

# Catch error message works now
try(plot(x50, dist.type="ecdf"))
```

## Warfarin


- **TODO:**
  - add to documentation
  - cov.scatter changed to covariates (default plot with covariates as in Brendel et al. 2010)
  - alternative: covsplit applied to the other types of graphs will produce graphs stratified by covariate categories/ranges
  - check npde.plot.scatterplot(wbase, which.x="cov", which.y="npde", which.cov="wt", bin.method="optimal") not rendering anything
```{r docVirWarf, echo=FALSE}
# Data
namfile<-file.path(docFigs,"doc_warfarin_data.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wbase,plot.type="data", main=" ", ylab="Warfarin concentrations (mg/L)")
if(saveDocPlots) dev.off()

# Default npde plots for base model
namfile<-file.path(docFigs,"doc_warfarin_basewaffle.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wbase)
if(saveDocPlots) dev.off()

# Fails - multiple arguments => should work and should call npde.plot.scatterplot
try(plot(wbase, plot.type="x.scatter", which.x="cov", which.y="npde", which.cov="wt"))
npde.plot.scatterplot(wbase, which.x="cov", which.y="npde", which.cov="wt", bin.method="optimal")

# Default npde plots for covariate model
namfile<-file.path(docFigs,"doc_warfarin_covwaffle.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wcov)
if(saveDocPlots) dev.off()

npde.plot.scatterplot(wcov, which.x="cov", which.y="npde", which.cov="wt", bin.method="optimal")

plot(wbase, plot.type="covariates", which.cov="wt")
plot(wbase, plot.type="covariates", which.cov="sex")
try(plot(wbase, plot.type="covariates", which.cov="age"))
plot(wbase, plot.type="ecdf", which.cov="sex", covsplit=TRUE)
plot(wbase, plot.type="ecdf", which.cov="wt", covsplit=TRUE)
plot(wcov, plot.type="ecdf", which.cov="wt", covsplit=TRUE)

# Density plots split by weight for both models
namfile<-file.path(docFigs,"doc_warfarin_ecdfBaseSplitWt.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wbase, plot.type="ecdf", which.cov="wt", covsplit=TRUE)
if(saveDocPlots) dev.off()

namfile<-file.path(docFigs,"doc_warfarin_ecdfCovSplitWt.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wcov, plot.type="ecdf", which.cov="wt", covsplit=TRUE)
if(saveDocPlots) dev.off()

# Splitting npde vs time plots by covariates
namfile<-file.path(docFigs,"doc_warfarin_baseSplitWt.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wbase, plot.type="x.scatter", covsplit=TRUE, which.cov=c("wt"))
if(saveDocPlots) dev.off()

namfile<-file.path(docFigs,"doc_warfarin_baseSplitSex.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wbase, plot.type="x.scatter", covsplit=TRUE, which.cov=c("sex"))
if(saveDocPlots) dev.off()

# Splitting npde vs time plots by covariates
namfile<-file.path(docFigs,"doc_warfarin_CovSplitWt.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov=c("wt"))
if(saveDocPlots) dev.off()

namfile<-file.path(docFigs,"doc_warfarin_CovSplitSex.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov=c("sex"))
if(saveDocPlots) dev.off()

# Covariate plots as boxplots (Brendel et al)
namfile<-file.path(docFigs,"doc_warfarin_boxCovWt.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(wcov, plot.type="covariates", which.cov=c("wt"))
if(saveDocPlots) dev.off()

# Reference profile compared to VPC
plot.tnpde<-plot(wcov, plot.type="x.scatter", ref.prof=list(id=2), main="tnpd with reference profile ID=2")
plot.vpc<-plot(wcov, plot.type="vpc", main="VPC")

namfile<-file.path(docFigs,"doc_warfarin_refprofile.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
grid.arrange(grobs=list(plot.tnpde, plot.vpc), nrow=1, ncol=2)
if(saveDocPlots) dev.off()

```

## Remifentanil (data will be on website)

Remove from documentation ?


```{r docRemifentanil, echo=FALSE}
if(FALSE) {
  xrem<-autonpde(namobs=file.path(fullDatDir,"remifent.tab"),namsim=file.path(fullDatDir,"simremifent_base.tab"),
iid=1,ix=2,iy=3,icov=c(6:12),namsav="remibase",units=list(x="hr",y="ug/L",
covariates=c("yr","-","cm","kg","m2","kg","yr")))
  plot(xrem)
  
  plot(xrem, plot.type="covariates", which.cov=c("LBM"))
  plot(xrem, plot.type="ecdf", covsplit=TRUE, which.cov=c("Age"))

}
```

## End of file, deactivating development mode

```{r deactivateDevMode, echo=FALSE, hide=T}
dev_mode()
```
