---
title: "Code integration"
author: "Emmanuelle Comets"
date: "21/01/2021"
output:
  pdf_document: default
  html_document: default
---

### Objective

Set up a debugging framework:
- load libraries
- load package functions individually
- prepare objects for debugging functions

### Defining folders, loading libraries

```{r setup, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(grid)
library(mclust)
library(testthat)
workDir<-"/home/eco/work/npde/npde30"
knitr::opts_chunk$set(root.dir = workDir)
notesDir<-file.path(workDir,"notebooks")
datDir<-file.path(workDir,"data")
fulldatDir<-file.path(workDir,"keep","data")
testsDir<-file.path(workDir,"tests","testthat")
setwd(workDir)
```

### Creating NpdeObject using the current version of the package

```{r setupOldPackage, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Classes from the package
source(file.path(workDir,"npde","R","aaa_generics.R"))
source(file.path(workDir,"npde","R","npdeControl.R"))
source(file.path(workDir,"npde","R","NpdeData.R"))
source(file.path(workDir,"npde","R","NpdeSimData.R"))
source(file.path(workDir,"npde","R","NpdeData-methods.R"))
source(file.path(workDir,"npde","R","NpdeRes.R"))
source(file.path(workDir,"npde","R","NpdeRes-methods.R"))
source(file.path(workDir,"npde","R","NpdeObject.R"))
source(file.path(workDir,"npde","R","NpdeObject-methods.R"))

# Computational functions from the package
source(file.path(workDir,"npde","R","compute_distribution.R"))
source(file.path(workDir,"npde","R","compute_npde.R"))
source(file.path(workDir,"npde","R","compute_pd.R"))
source(file.path(workDir,"npde","R","compute_ploq.R"))
source(file.path(workDir,"npde","R","mainNpde.R"))
source(file.path(workDir,"npde","R","npde.R"))

# Plot functions from the package - kept, some changes
source(file.path(workDir,"npde","R","plotNpde-methods.R"))
source(file.path(workDir,"npde","R","plotNpde-plotFunctions.R"))
source(file.path(workDir,"npde","R","plotNpde-auxScatter.R")) 
source(file.path(workDir,"npde","R","plotNpde-auxScatterPlot.R")) 
source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
source(file.path(workDir,"npde","R","plotNpde-distributionPlot.R")) # extracted "main" for distribution plots from plotNpde-plotFunctions.R
source(file.path(workDir,"npde","R","plotNpde-scatterplot.R")) # extracted "main" for scatter plots f
source(file.path(workDir,"npde","R","plotNpde-binningPI.R")) # renamed from plotNpde-unitFunctionsPI.R
source(file.path(workDir,"npde","R","plotNpde-covplot.R")) # covariate plots as boxplots
```

### Run npde

- theophylline
- viral load (different)
- warfarin (2 models, covariates)

```{r runNpdeTheo, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}

theofit1<-autonpde(file.path(datDir, "theopp.tab"),namsim=file.path(datDir, "simtheopp.tab"),1,3,4,boolsave=FALSE, units=list(x="hr",y="mg/L"))

# Warfarin data, using files on disk
wbase<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(fulldatDir, "simwarfarinBase.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")), boolsave=FALSE)

wcov<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(fulldatDir, "simwarfarinCov.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")), boolsave=FALSE)

# Warfarin with MDV
warfmdv<-read.table(file.path(datDir, "warfarin.tab"), header=TRUE)
idx<-sample(1:dim(warfmdv)[1], 10)
warfmdv$mdv<-0
warfmdv$mdv[idx]<-1
expect_equal(sum(warfmdv$mdv),10)

wmdv<-autonpde(namobs=warfmdv,namsim=file.path(fulldatDir, "simwarfarinCov.tab"), iid=1,ix=2,iy=4,imdv=9,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

```

```{r runNpdeVIH, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
virload<-read.table(file.path(datDir, "virload.tab"), header=TRUE)
virload20<-read.table(file.path(datDir, "virload20.tab"), header=TRUE)
virload50<-read.table(file.path(datDir, "virload50.tab"), header=TRUE)
simvirload<-read.table(file.path(fulldatDir, "simvirload.tab"), header=TRUE)

yvir1<-autonpde(virload,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))

yvir20<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE)

yvir2<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE)

yvir50<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE)

# Different methods to handle LOQ
yvir50.omit<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="omit")

yvir50.ppred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="ppred")

yvir50.ipred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4, iipred=5, boolsave=FALSE, cens.method="ipred")

# noms ds ecoDocPlots.Rmd
xvir<-yvir1
x20<-yvir20
x50<-yvir50
x50.ipred<-yvir50.ipred
x50.omit<-yvir50.omit
x50.ppred<-yvir50.ppred
```

### Debugging 

#### Main plots

```{r yloq, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
plot(yvir20)

plot(yvir20, plot.type="x.scatter")

plot(yvir20, plot.type="pred.scatter")

plot(yvir20, plot.type="hist")

plot(yvir20, plot.type="qqplot")

plot(yvir20, plot.type="vpc")

plot(yvir20, plot.type="loq")

hist20<-plot(yvir20, plot.type="hist")
xscatter20<-plot(yvir20, plot.type="x.scatter")
predscatter20<-plot(yvir20, plot.type="pred.scatter")
qqplot20<-plot(yvir20, plot.type="qqplot")
list_plot<-list(hist20, qqplot20, xscatter20, predscatter20)

grid.arrange(grobs = list_plot,nrow=2, ncol=2,vjust = 1, gp = gpar(fontsize=yvir20@prefs$size.main))

plot(yvir20, plot.type="ecdf", bands=TRUE, approx.pi=TRUE)
```

#### Final plots

```{r debugHist, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
plot(wcov, plot.type="hist")
plot(wcov, plot.type="ecdf")

npdeObject <- wcov
# Plot options
userPlotOptions <- npdeObject@prefs
plot.opt <- set.plotoptions.default( npdeObject )
plot.opt <- modifyList( plot.opt, userPlotOptions[ intersect( names( userPlotOptions ), names( plot.opt ) ) ] )
sim.ypl<-NULL

# Creating obsmat for distribution plots (hist, qqplot, ecdf)
if(length(npdeObject["data"]["icens"])>0) has.cens<-TRUE else has.cens<-FALSE
covsplit<-plot.opt$covsplit
if(covsplit) {
    if(is.numeric(plot.opt$which.cov)) plot.opt$which.cov<-npdeObject["data"]["name.covariates"][plot.opt$which.cov] # convert to names of covariates
    if(plot.opt$which.cov=="all" | plot.opt$which.cov=="") plot.opt$which.cov<-npdeObject["data"]["name.covariates"]
}
if (length(npdeObject["data"]["name.covariates"])>0) hasCovariates = TRUE else hasCovariates = FALSE

ypl<-npdeObject["results"]["res"]$npde

obsmat<-data.frame(x=ypl)
obsmat$category<-"all"
if(length(npdeObject["data"]["icens"])>0) obsmat$cens<-npdeObject["data"]["data"]$cens else obsmat$cens<-0
not.miss = npdeObject["data"]["not.miss"] # not.miss : not missing data in the data TRUE/FALSE
obsmat<-obsmat[not.miss,]
if(sum(is.na(obsmat$x))>0) {# missing data because of omit method
  not.miss2<-!(is.na(obsmat$x))
  obsmat<-obsmat[not.miss2,]
  if(!is.null(sim.ypl)) sim.ypl<-sim.ypl[rep(not.miss2, nsim)]
}  else not.miss2<-NULL


# histogram
aux.npdeplot.hist(obsmat,  plot.opt, distrib="norm", nclass=10, sim.ypl=NULL)

# QQplot and ecdf
dist.type <- "qqplot"
aux.npdeplot.dist(obsmat,  plot.opt, dist.type=dist.type, distrib="norm", sim.ypl=NULL)

dist.type <- "ecdf"
aux.npdeplot.dist(obsmat,  plot.opt, dist.type=dist.type, distrib="norm", sim.ypl=NULL)

if(FALSE) {
  which="npd"
  npdeObject <- wcov
  dist.type <- "ecdf"
  }

```

#### Why do the bands on npd/npde appear at less than +/- 1.96 ?

Because we have limited data in each bin (with N=12, we expect +/- 1.43, with N=20, +/- 1.63, and we converge to -1.96 by around 100 observations per bin)...

```{r checkBands}
theofit1@prefs$vpc.interval

# bands
bnds1<-compute.bands(200)
bnds2<-compute.bands(1000)
bnds1$bmed
bnds2$bmed

bnds12<-compute.bands(12)
bnds12$bmed
bnds20<-compute.bands(20)
bnds20$bmed

# Plot showing how we converge slowly to 1.96 :-)
cbnds <- compute.bands(seq(0,200))
plot(seq(0,200),cbnds$bmed[,3], type="l")
abline(h=1.5)
abline(h=1.96)

# PI computed
yfit <- theofit1
which.x <- "x"
which.y <- "npde"
obsmat <- data.frame(x=switch(which.x, "x"=yfit@data@data[,yfit@data@name.predictor],
                              "pred"=yfit@results@res$ypred,
                              "cov"=yfit@data@data[,yfit@data@name.covariates[idx.cov[1]]] ))
obsmat$y <- switch(which.y, "npde"=yfit@results@res$npde, "npd"=yfit@results@res$npd, "pd"=yfit@results@res$pd,
                     "yobs"=yfit@results@res$ycomp, "pde"=yfit@results@res$npde)

#if(length(yfit@data@icens)==0) obsmat$cens<-0 else obsmat$cens<-yfit@data@data$cens
obsmat$cens<-0
obsmat$category<-'none'
# test if censored data
not.miss = yfit["data"]["not.miss"] # not.miss : not missing data in the data TRUE/FALSE
obsmat<-obsmat[not.miss,]

xbin<-npde.binning(obsmat$x,plot.opt=yfit@prefs)
obsmat$grp <- xbin$xgrp
matbin<-data.frame(grp=1:length(xbin$xcent), xcent=xbin$xcent, binlabel = names(xbin$xcent)) # binning matrix

bnds<-aux.npdeplot.computepi(obsmat)
pimat<-aux.npdeplot.pimat(obsmat, xcent=matbin$xcent)
# pinf.median, psup.median -/+ 1.44 au lieu de 1.96, why ?

```


#### dispatching function

Not run, contains relative paths.

```{r troispetitspoints, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
if(FALSE) {
  test_file(file.path(testsDir,"test-arguments-ellipsis.R"))
  
  test_file(file.path(testsDir,"test-modifyOptions.R"))
  
}

```

#### covariate plots

```{r covariate, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
npde.plot.scatterplot(wcov, which.x="cov", which.y="npd", which.cov="wt")

npdeObject<-wcov
plot.opt<-wcov@prefs
which.x<-"cov"
which.y<-"npd"
plot.opt$which.cov<-"wt"
ref.prof<-NULL

```

#### distribution plots

Plots omitting LOQ data - expect to see a lot of red

```{r debugSetup, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
npde.plot.dist(yvir50.omit)
npde.plot.dist(yvir50.omit, dist.type="ecdf")
npdeObject<-yvir50.omit
which<-"npde"
plot.opt<-yvir50.omit@prefs

npde.plot.scatterplot(yvir50.omit)
npdeObject<-yvir50.omit
plot.opt<-yvir50.omit@prefs
which.x<-"x"
which.y<-which
ref.prof<-NULL

npde.plot.scatterplot(yvir50.omit)
plot(yvir50.omit, plot.type="x.scatter")

```

### Arguments to plot function

```{r debugArgs, echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}

plot.NpdeObject2 <- function(x, y, ...) {
  
  args1<-match.call(expand.dots=TRUE)
  list.args <- list(...)
  list.args<-list.args[!(names(list.args) %in% c("dist.type", "which.x", "which.y", "which"))]
  force.new<-"new"
  list.args$npdeObject <- x
  list.plot.qqplot = list()
  list.args$dist.type<-"qqplot"
  list.args$new <- force.new
  typmet<-"npde"
  for(imet in typmet) {
    list.args$which <- typmet
    list.plot.qqplot[[imet]] <-do.call(npde.plot.dist, list.args)
  }
  if(length(typmet)==1) list.plot.qqplot<-list.plot.qqplot[[1]]
  return(list.plot.qqplot)
}

x<-plot.NpdeObject2(theofit1, dist.type="qqplot")


```
