---
title: "Generating plots in the documentation (section Examples)"
author: "Emmanuelle Comets"
date: "02/02/2021"
output:
  pdf_document: default
  html_document: default
---


## Objective

Generate the plots for the LaTeX user guide

## Setup

### loading libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(mclust)
library(testthat)
# library(grid)
workDir<-"/home/eco/work/npde/npde30"
fullDatDir<-file.path(workDir,"keep","data") # Full data files (some removed from package to decrease size on CRAN)
knitr::opts_chunk$set(root.dir = workDir)
docFigs<-"/home/eco/work/npde/doclib/figs"
saveDocPlots<-FALSE
```

### Install package in development mode
  
```{r devModeInstall}
dev_mode() # development mode
install.packages(pkgs=file.path(workDir,"npde_3.0.tar.gz"),repos=NULL)
library(npde)
```

### Run examples

- remove warnings (name.ipred empty, etc...)  **Romain**

```{r theoRun, echo=FALSE}
# Calling autonpde with dataframes
data(theopp)
data(simtheopp)
theofit<-autonpde(theopp,simtheopp,1,3,4,boolsave=FALSE, units=list(x="hr",y="mg/L"))

# Viral load
data(virload)
data(virload20)
data(virload50)
data(simvirload)

# full data
if(FALSE) xvir<-autonpde(virload,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))
# cdf method
if(FALSE) x20<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))
x50<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))

# Different methods to handle LOQ
x50.omit<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="omit", units=list(x="hr", y="cp/mL, log 10 base"))
x50.ppred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="ppred", units=list(x="hr", y="cp/mL, log 10 base"))
x50.ipred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4, iipred=5, boolsave=FALSE, cens.method="ipred", units=list(x="hr", y="cp/mL, log 10 base"))

# Warfarine
data(warfarin)
data(simwarfarinCov)
simbase<-read.table(file.path(fullDatDir, "simwarfarinBase.tab"), header=TRUE)

wbase<-autonpde(namobs=warfarin,namsim=simbase, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

wcov<-autonpde(namobs=warfarin,namsim=simwarfarinCov, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfCov", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

```

## Theophylline example

- data
  - le plot(npdeData) ne marche pas **Romain**
  - pour faire un graphe il faut passer par *plot.type="data"* ou *npde.plot.data()*
  - name of ylab wrong  **Eco fait**
- VPC, scatterplot  **Eco fait**
  - modifié pour que le tracé des percentiles observés soit fait avec les linetype et size de lobs (pas des bandes), par contre la couleur matche celle de la bande de prédiction correspondante

```{r docTheo, echo=FALSE}

plot(theofit@data) # ne marche pas

# Raw data
namfile<-file.path(docFigs,"doc_theodata_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
#  plot(theofit@data, plot.loq=FALSE, size.pobs=2)
plot(theofit, plot.type="data")
# plot(theofit, plot.type="data", size.pobs=2, xlab="Time (hr)",ylab="Theophylline concentrations (mg/L)")
if(saveDocPlots) dev.off()

# Default waffle plot
namfile<-file.path(docFigs,"doc_theodefault_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(theofit)
if(saveDocPlots) dev.off()

# VPC
namfile<-file.path(docFigs,"doc_theovpc_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(theofit, plot.type="vpc")
if(saveDocPlots) dev.off()

```

## Viral load example

- data
  - mêmes problèmes que plus haut
  - LOQ data should be plotted  **Romain**
  - besoin de faire un waffle plot avec les 4 objets data, **Romain TODO** possible ? (sinon sauver 4 graphes)
  - complete data according to the censoring method when an npdeObject is given (plot just the LOQ data when the plot is called directly on a npdeData object) **Romain**

```{r docVirloadData, echo=FALSE}
# p1<-npde.plot.data(x50, plot.default=TRUE) # non, c'est pas ça
# Raw data
namfile<-file.path(docFigs,"doc_data50_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", line.loq=TRUE, ylim=c(0,6.5))
plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", plot.loq=FALSE, line.loq=TRUE, ylim=c(0,6.5))
plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", impute.loq=FALSE, line.loq=TRUE, ylim=c(0,6.5))
plot(x50.ipred, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", line.loq=TRUE, ylim=c(0,6.5))
if(saveDocPlots) dev.off()

# Romain ?
if(FALSE) {
  p1<-plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)")
  p2<-plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", plot.loq=FALSE)
  p3<-plot(x50, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)", impute.loq=FALSE)
  p4<-plot(x50.ipred, plot.type="data", xlab="Time (hr)", ylab="log(Viral load) (cp/mL)")
  grid.arrange(list(p1,p2,p3,p4), nrow=2, ncol=2)
}

```

- scatterplots and VPC
  - pb with VPC of x50  **Eco fait**
- possibilité d'utiliser un grid.arrange pour les 2 derniers graphes  ?  **Romain**
- VPC missing tite on y-axis
  
```{r docVirload, echo=FALSE}
# Diagnostics plots, cdf method (default)
namfile<-file.path(docFigs,"x50_cdf_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50)
if(saveDocPlots) dev.off()
# Diagnostics plots, omit method
namfile<-file.path(docFigs,"x50_omit_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.omit)
if(saveDocPlots) dev.off()
# Diagnostics plots, ipred method
namfile<-file.path(docFigs,"x50_ipred_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.ipred)
if(saveDocPlots) dev.off()
# Diagnostics plots, ppred method
namfile<-file.path(docFigs,"x50_ppred_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.ppred)
if(saveDocPlots) dev.off()
# VPC
namfile<-file.path(docFigs,"doc_vpc50_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50,plot.type="vpc", line.loq=TRUE)
plot(x50.omit,plot.type="vpc")
if(saveDocPlots) dev.off()

# Scatterplot
namfile<-file.path(docFigs,"virload_xscatter_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
plot(x50.omit,plot.type="x.scatter")
plot(x50,plot.type="x.scatter")
if(saveDocPlots) dev.off()

```

- P(Y<LOQ): changed defaults
- todo: catch error message when using dist.type="ecdf" instead of plot.type="ecdf" (not sure what's happening) **Romain**

```{r docVirloadLOQ, echo=FALSE}

# P(Y<LOQ)
namfile<-file.path(docFigs,"virload_ploq_gg.eps")
if(saveDocPlots) cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
try(plot(x50,plot.type="loq", main=" "))
if(saveDocPlots) dev.off()

# Catch error message
try(plot(x50, dist.type="ecdf"))
```

## Warfarine


- **TODO:**
  - add to documentation
  - default plot with cov.scatter should be boxplot => check why not working

```{r docVirWarf, echo=FALSE}

plot(wbase)

plot(wbase, plot.type="cov.scatter")

plot(wbase, plot.type="x.scatter", covsplit=TRUE, which.cov=c("sex","wt"))

```

## Remifentanil (data will be on website)

Remove from documentation ?


```{r docRemifentanil, echo=FALSE}
if(FALSE) {
  xrem<-autonpde(namobs=file.path(fullDatDir,"remifent.tab"),namsim=file.path(fullDatDir,"simremifent_base.tab"),
iid=1,ix=2,iy=3,icov=c(6:12),namsav="remibase",units=list(x="hr",y="ug/L",
covariates=c("yr","-","cm","kg","m2","kg","yr")))
  plot(xrem)
  
  plot(xrem, plot.type="cov.scatter", which.cov=c("LBM"))
  plot(xrem, plot.type="ecdf", covsplit=TRUE, which.cov=c("Age"))

}
```

## End of file, deactivating development mode

```{r deactivateDevMode, echo=FALSE, hide=T}
dev_mode()
```
