---
title: "Testing package with devtools"
author: "Emmanuelle Comets"
date: "02/02/2021"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

## Notes before release

- package
  -  **TODO** automatically load libraries when loading *npde* ()
    - ggplot2 not loaded, gridExtra, mclust not loaded
    - check: mclust
  - compilation: compiled package as npde 3.0
    - version number 3.0 because reference profiles included
    - lots of error messages for "no visible binding for global variable" in variables related to ggplot2 (Undefined global functions or variables) => hope this does not block us for CRAN
- TODO *npde website* (bookdown, Eco)
- code **TODO** for 3.1
  - add an option to remove all output when required and remove warnings if requested
  - plot for a NpdeData object
    - change index labels to allow duplicate time points
- **TODO** simplify output for *show()* function (v3.0 or v3.1 ?)

## Setup, loading libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(mclust)
library(testthat)
library(grid)
workDir<-"/home/eco/work/npde/npde30/"
setwd(workDir)
knitr::opts_chunk$set(root.dir = workDir)
#docFigs<-"/home/eco/work/npde/doclib/figs"
saveDocPlots<-FALSE
savePaperPlots<-FALSE
```

### Install package in development mode
  
```{r devModeInstall}
dev_mode() # development mode
install.packages(pkgs=file.path(workDir,"npde_3.0.tar.gz"),repos=NULL)
library(npde)
```


```{r virloadRun, echo=FALSE}
#Viral load data
data(virload20)
data(simvirload)

yvir20<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE)
yvir20.omit<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE, cens.method="omit")

plot(yvir20)
plot(yvir20, plot.type="loq")
```

```{r grid.arrange, echo=FALSE}
plot.x.scatter.yvir20 = plot(yvir20,plot.type="x.scatter")
plot.pred.scatter.yvir20 = plot(yvir20,plot.type="pred.scatter")
grid.arrange(grobs=list(plot.x.scatter.yvir20, plot.pred.scatter.yvir20), nrow=1, ncol=2)

plot.vpc.yvir20 = plot(yvir20,plot.type="vpc")
plot.yvir20.omit = plot(yvir20.omit,plot.type="vpc")
grid.arrange(grobs=list(plot.vpc.yvir20,plot.yvir20.omit), nrow=1, ncol=2)

```

## End of file, deactivating development mode

```{r deactivateDevMode, echo=FALSE, hide=T}
dev_mode()
```

