---
title: "Reference profiles"
author: "Emmanuelle Comets"
date: "12/01/2021"
output:
  pdf_document: default
  html_notebook: default
---

**Warning: old code, not for new version**

## Objective

- create datasets for the test files for functions 
  - binning: npde.binning
  - plotting VPC and npde scatterplots: 
  - computing reference profile: aux.npdeplot.meanprof, *transform mean profile*
  - computing prediction intervals: compute.bands, compute.bands.true, aux.npdeplot.computepi
- files needed for these different steps:
  - observed data (aka original data): **obsdat_** [eg *obsdat_ecopk*]
  - simulated data (simulations under the model using the design in the original dataset) **simdat_** [eg *simdat_ecopk*]
    - for convenience, also save a matrix with npde~N(0,1) (used to compute PI) of nrow=nrow(obsdat): **npdesim_** [eg *npdesim_ecopk*]
  - obsmat for npde, yobs, tnpde for some reference profile (eg dose=1000): **obsmat_**
  - pimat for npde, yobs, tnpde for some reference profile (eg dose=1000): **pimat_**

## Setup, loading libraries

```{r setup, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(grid)
library(testthat)
#workDir<-"D:/RECHERCHES/_NPDE/Npde-2021/npde30-main"
workDir<-"/home/eco/work/npde/npde30"
notesDir<-file.path(workDir,"notebooks")
testsDir<-file.path(workDir,"npde","tests","testthat")
provDir<-file.path(workDir,"kompareCode") # Code change, temporary folder and files (Eco)
setwd(workDir)
createDat<-FALSE

#source(file.path(workDir,"npde","R","computePI.R"))
source(file.path(workDir,"npde","R","plotNpde-unitFunctionsPI.R"))
source(file.path(workDir,"npde","R","plotNpde-unitFunctionsRef.R")) # aux.npde.plot(), version Romain
source(file.path(workDir,"npde","R","npdeControl.R"))
```

### Example saved by Romain

- 3 categories of weight => need a more simple example without covsplit
  - also would need the same Y-axis (ie facet_grid plot) and not 3 separate plots => maybe make a second version outputting a single plot instead of a list of plots, with facet_grid
  - not a very good example as the PI overlap
  - plot with the 3 categories and with just one => works
- changed graphical options to default as was just too hideous
- a number of issues
  - pb with censored data being overlayed on the plot in excess
  - labels

```{r exampleRomain,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# data : xtheo_cens
obsmat <- readRDS(file.path(testsDir, "obs_mat_xtheo_cens.rds"))
pimat <- readRDS(file.path(testsDir, "pi_mat_xtheo_cens.rds"))
plot.hideous <- readRDS(file.path(testsDir, "plot_opt_xtheo_cens_scatter.rds"))
# changement des options, c'est hideux
plot.opt2<-set.plotoptions.default()
plot.opt2$xaxis<-plot.hideous$xaxis
plot.opt2$xlab<-plot.hideous$xlab
plot.opt2$ylab<-plot.hideous$ylab
plot.opt2$xunits<-plot.hideous$xunits
plot.opt2$yunits<-plot.hideous$yunits
plot.opt2$which.cov<-plot.hideous$which.cov
plot.opt<-plot.opt2

aux.npdeplot.plot(obsmat, pimat, plot.opt2)

aux.npdeplot.plot(obsmat[obsmat$cov==obsmat$cov[1],], pimat[pimat$category==pimat$category[1],], plot.opt)

vec<-rnorm(10000,0,1)
quantile(vec,c(0.025,0.5,0.975))

```

### Sourcing new changes and plotting the same data with new code

**Debugging aux.npdeplot.plot**

- **Problems**
  - binf, bsup should be lower and upper bounds of PI, but then bmed should be the median (ie theoretical) value OR binf, bsup, bmed are the 3 PI, and 0025, 05 and 0975 are the respective percentiles for each pi
  - is dotline useful ? (either use quantile or fill quantile with theoretical value)
  - need the same names in both pimat and obsmat to be less confusing
    - for groups = should be grp, but **change to xbin** (because grp and group could be covariate names)
    - why is category different than cov and why is there also covariate ?
    - xcent: ok as name of bin center
  - we don't need covariates and category both, this function is only supposed to be called with one covariate at a time (the split is done in the function calling it)
- **TODO** change name or remove dotline, should be ther + names not consistent
  - type of pi: pinf, pmid, psup (3 PI, eg 0.025, 0.5 and 0.975 for 95% PI, controlled by vpc.interval)
  - boundaries of pi: lower, median, upper
  - => pinf.lower, pinf.median, pinf.upper, etc...
  - grouping factor: grp for both obsmat and pimat
  - x-value for bin: xcent (ok)
  - observed percentiles: obs.inf obs.med obs.sup
  - removed dotline

```{r sourceChanges,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
source(file.path(provDir,"computePI.R")) # aux.npdeplot.computepi(), aux.npdeplot.meanprof(), transform PI
source(file.path(provDir,"aux.npde.plot.R")) # aux.npde.plot(), version Eco

# match covariate levels in the two datasets
levels(obsmat$cov)<-levels(pimat$category)
obsmat<-obsmat[,c(1,2,4,5,3,6)]
colnames(obsmat)[4]<-"category"

colnames(pimat)[1]<-"grp"
colnames(pimat)[5:16]<-c("pinf.lower","pmid.lower","psup.lower","pinf.median", "pmid.median", "psup.median","pinf.upper","pmid.upper","psup.upper","obs.inf","obs.median","obs.sup")
pimat<-pimat[,c(1,4,2,5:16)]

# Plot all 3 categories of Wt
aux.npdeplot.plot.eco(obsmat, pimat, plot.opt)

# Plot only one category
icat<-as.character(pimat$category[1])
obsmat.cov<-obsmat[obsmat$category==icat,]
aux.npdeplot.plot.eco(obsmat.cov, pimat[pimat$category==icat,], plot.opt)

if(createDat) { # Saving Romain's files to new format for files
  saveRDS(obsmat,file.path(notesDir,"eco_obsmat_xtheoWt.rds"))
  saveRDS(pimat,file.path(notesDir,"eco_pimat_xtheoWt.rds"))
  saveRDS(plot.opt,file.path(notesDir,"eco_plotopt_xtheoWt.rds"))
}
```

### Checking a few options

- plot.box=TRUE
  - fails miserably with Japanese warnings :-)
  - seems to be missing some boxes (only 6 and should be 10, ie 5 doesn't show (or maybe does but flat ?))
  - prediction intervals don't show and only weird lines appear
- check the labels for the different options (x, pred, cov, ...)

```{r checks,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# plot.box - plot scatter as boxplots
plot.opt$plot.box<-TRUE
aux.npdeplot.plot.eco(obsmat.cov, pimat[pimat$category==icat,], plot.opt)

## Plot all 3 categories of Wt
aux.npdeplot.plot.eco(obsmat, pimat, plot.opt)

# Covariate plot with "cov" option - TODO 
plot.opt$plot.box<-FALSE

# Check labels - TODO

```

## One-compartment PK example with covariates, different doses and different sampling schedules

### Creating datafile

- one-compartment PK model:
  - parameters: ka~LN(2,0.2), V~LN(V_0,0.2), CL~LN(CL_0, 0.2) (20% IIV)
  - covariate effects: V_0(sex=0)=10, V_0(sex=1)=6; CL_0= 1 + 0.3*log(age/40)
- design:
  -  100 subjects: 50 male, 50 female, age ranging from 30 to 70
  - 5 groups, in each group, following time sequences: 20 subjects with full (2-24 every 2h), 20 initial (1-6h then 12, 24), 10 sparse (1, 2, 5, 10, 24)
  - doses: c(10,20,50,100,1000) cycling every 5 subjects
- save to or read from file (save once with createDat set to TRUE)

```{r createDataset,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
nrep<-200 # nb of simulations

# Creating dataRef with different number of observations per subject
if(createDat) {
  onecpt<-function(t, dose, ka, V, CL)
  dose/V*ka/(ka-CL/V)*(exp(-CL/V*t) - exp(-ka*t))
ageseq<-seq(20.5,70,0.5)
sexseq<-rep(c(0,1),50)
doseseq<-rep(c(10,20,50,100,1000),20)
timeseq<-list(c(0.5,1,seq(2,24,2)), c(seq(1,6),12,24), c(0.5,1,2,5,10,24))
itimeseq<-rep(c(rep(1,20),rep(2,20),rep(3,10)),2)
kai<-2*exp(rnorm(100,sd=0.2))
etaV<-rnorm(100,sd=0.2)
Vi<-(10*(1-sexseq)+6*sexseq)*exp(etaV)
etaCl<-rnorm(100,sd=0.2)
Cli<- (1+0.3*log(ageseq/40))*exp(etaCl)

dataRef<-NULL
for(i in 1:100) {
  xtim<-timeseq[[itimeseq[i]]]
  dataRef<-rbind(dataRef,
                data.frame(id=i,time=xtim,y=onecpt(xtim,doseseq[i], kai[i], Vi[i], Cli[i]),sex=sexseq[i],age=ageseq[i], dose=doseseq[i]))
}
# plot(dataRef$time,dataRef$y)
# xtim<-seq(0,24,2)
# plot(xtim,onecpt(xtim,100, 2, 10, 1),type="l")

# Creating simulated data with the same structure as dataRef, from the same model
matsim<-NULL
for(irep in 1:nrep) {
  kai<-2*exp(rnorm(100,sd=0.2))
  etaV<-rnorm(100,sd=0.2)
  Vi<-(10*(1-sexseq)+6*sexseq)*exp(etaV)
  etaCl<-rnorm(100,sd=0.2)
  Cli<- (1+0.3*log(ageseq/40))*exp(etaCl)
  for(i in 1:100) {
    xtim<-timeseq[[itimeseq[i]]]
    matsim<-rbind(matsim,
                  data.frame(irep=irep,id=i,time=xtim,y=onecpt(xtim,doseseq[i], kai[i], Vi[i], Cli[i])))
  }
}
# adding covariate
matsim$sex<-rep(dataRef$sex,nrep)
matsim$age<-rep(dataRef$age,nrep)
matsim$dose<-rep(dataRef$dose,nrep)
npdesim<-dataRef[,c(1,2)]
npdesim$npde<-rnorm(dim(npdesim)[1],0,1) # simulating from N(0,1) to create npde
npdesim$pd<-pnorm(npdesim$npde)
# plot(matsim$time,matsim$y)

# Saving to disk
  saveRDS(dataRef,file.path(notesDir,"obsdat_ecopk.rds"))
  saveRDS(matsim,file.path(notesDir,"simdat_ecopk.rds"))
  saveRDS(npdesim,file.path(notesDir,"npdesim_ecopk.rds"))
} else { # Read from disk
  dataRef<-readRDS(file.path(notesDir,"obsdat_ecopk.rds"))
  matsim<-readRDS(file.path(notesDir,"simdat_ecopk.rds"))
  npdesim<-readRDS(file.path(notesDir,"npdesim_ecopk.rds"))
}

# Unique times, grouping matrix for the examples below
nrep<-dim(matsim)[1] / dim(dataRef)[1]
xtim<-unique(dataRef$time)
grmat<-data.frame(xat=sort(xtim), grp=1:length(xtim))
dataRef$grp<-grmat$grp[match(dataRef$time,grmat$xat)]
matsim$grp<-rep(dataRef$grp,nrep)

plot.opt2<-set.plotoptions.default()
```

### Computing PI for a VPC using the same data

Creating the PI to plot a VPC, using all times

- across all doses (very large)
- PI only for the dose=1000 group (but will still have covariate effects, uncorrected here (could correct using pcVPC))

```{r piVPC,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Over all doses
alpha<-0.025; pi.size<-0.95
xcal<-aux.npdeplot.computepi(dataRef, quantiles=c(alpha, 0.5, 1-alpha), pi.size=pi.size, approx.pi=FALSE, sim.ypl=matsim$y)

vpc.piall<-data.frame(xcent=sort(unique(dataRef$time)))
for(i in c(1,3,2))
  vpc.piall<-cbind(vpc.piall, xcal[[i]][,2:4])
qmat<-tapply(dataRef$y,dataRef$time,quantile,c(alpha,0.5,1-alpha))
vpc.piall<-cbind(vpc.piall, matrix(unlist(qmat), ncol=3, byrow=TRUE))
colnames(vpc.piall)[2:13]<-c("pinf.lower","pmid.lower","psup.lower","pinf.median", "pmid.median", "psup.median","pinf.upper","pmid.upper","psup.upper","obs.inf","obs.median","obs.sup")

# Over dose=1000 only
xcal2<-aux.npdeplot.computepi(dataRef[dataRef$dose==1000,], quantiles=c(alpha, 0.5, 1-alpha), pi.size=pi.size, approx.pi=FALSE, sim.ypl=matsim$y[matsim$dose==1000])

vpc.pi1000<-data.frame(xcent=sort(unique(dataRef$time)))
for(i in c(1,3,2))
  vpc.pi1000<-cbind(vpc.pi1000, xcal2[[i]][,2:4])
qmat<-tapply(dataRef$y[dataRef$dose==1000],dataRef$time[dataRef$dose==1000],quantile,c(alpha,0.5,1-alpha))
vpc.pi1000<-cbind(vpc.pi1000, matrix(unlist(qmat), ncol=3, byrow=TRUE))
colnames(vpc.pi1000)[2:13]<-c("pinf.lower","pmid.lower","psup.lower","pinf.median", "pmid.median", "psup.median","pinf.upper","pmid.upper","psup.upper","obs.inf","obs.median","obs.sup")

if(createDat) {
  saveRDS(vpc.pi1000,file.path(notesDir,"pimat_vpc1000_ecopk.rds"))
  saveRDS(vpc.piall,file.path(notesDir,"pimat_vpcall_ecopk.rds"))
} else { # Read from disk
  vpc.pi1000<-readRDS(file.path(notesDir,"pimat_vpc1000_ecopk.rds"))
  vpc.piall<-readRDS(file.path(notesDir,"pimat_vpcall_ecopk.rds"))
}

```

## Using new code to plot scatterplots and VPC on simulated data

### Binning 

**TODO** create unitary tests for binning (including different binning methods +++) + advice on binning for *pred*

```{r binning,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Bin values on the x-axis in 10 categories
xbin<-npde.binning(npdesim$time,plot.opt,verbose=FALSE)
npdesim$grp<-xbin$xgrp
print(data.frame(xaxt=xbin$xat, grp=1:10))

# Use natural bins (ie 16 groups)
npdesim$grp<-dataRef$grp
```

### Creating pimat for the npde

Compute PI, using simulated values for npde in N(0,1)

```{r computePIapprox,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Compute the PI on selected quantiles using simulated values npde~N(0,1)
pi.size<-plot.opt$pi.size
alpha <- (1 - plot.opt$vpc.interval) / 2
if(alpha>0.5) alpha<-(1-alpha)

xcal<-bnds<-aux.npdeplot.computepi(npdesim, quantiles=c(alpha, 0.5, 1-alpha), pi.size=pi.size, distrib="norm", approx.pi=TRUE, sim.ypl=NULL)

# 90% PI with pi.size also 90%
bnds2<-aux.npdeplot.computepi(npdesim, quantiles=c(0.1, 0.5, 0.9), pi.size=0.9, distrib="norm", approx.pi=TRUE, sim.ypl=NULL)

# Create pimat with new names
## PI for npde
pimat<-data.frame(grp=unlist(bnds$binf[,"grp"]), xcent=sort(unique(npdesim$time)))
pimat$category<-"none"
for(i in c(1,3,2))
  pimat<-cbind(pimat, bnds[[i]][,2:4])
## Empirical percentiles on npdesim (simulated npde)
pimat<-cbind(pimat,matrix(unlist(tapply(npdesim$npde,npdesim$grp,quantile,c(0.025, 0.5, 0.975))), ncol=3, byrow=TRUE))
colnames(pimat)[4:15]<-c("pinf.lower","pmid.lower","psup.lower","pinf.median", "pmid.median", "psup.median","pinf.upper","pmid.upper","psup.upper","obs.inf","obs.median","obs.sup")
print(pimat)
if(createDat) {
  saveRDS(pimat,file.path(notesDir,"pimat_npde_ecopk.rds"))
}

# Corresponding percentiles for npd instead of npde 
pimat2<-pimat
pimat2[13:15]<-matrix(unlist(tapply(npdesim$npd,npdesim$grp,quantile,c(0.025, 0.5, 0.975))), ncol=3, byrow=TRUE)
if(createDat) {
  saveRDS(pimat2,file.path(notesDir,"pimat_npd_ecopk.rds"))
}

######## deprecated
# Create pimat2 with same names as Romain
if(FALSE) {
  l <- list(xcal$bnds$xcent,xcal$bnds$binf,xcal$bnds$bmed,xcal$bnds$bsup)
  pimat2 <- as.data.frame(Reduce(cbind,l),check.names = TRUE)


  
  pimat2<-cbind(pimat2, matrix(unlist(tapply(npdesim$npde,npdesim$grp,quantile,c(0.025, 0.5, 0.975))), ncol=3, byrow=TRUE))
  colnames(pimat2)[14:16]<-colnames(pimat[14:16])
  
  pimat2$dotline.min<-qnorm(0.025)
  pimat2$dotline.med<-qnorm(0.5)
  pimat2$dotline.max<-qnorm(0.975)
}


```

### Create corresponding obsmat and plot result

```{r plotPInpde,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Create obsmat
obsmat<-npdesim[,c(5,2,3)]
colnames(obsmat)<-c("grp","x","y")
obsmat$category<-"none"
obsmat$cens<-0
obsmat$loq<-0
# Plot
plot.opt$which<-"npde"
plot.opt$which<-"npde"
aux.npdeplot.plot.eco(obsmat, pimat, plot.opt)

if(createDat) {
  saveRDS(obsmat,file.path(notesDir,"obsmat_npde_ecopk.rds"))
}
```


## Reference profiles

Testing the function to compute the reference profile with different options:
- reference profiles for the different doses, shown as facet graph

### Reference profiles across different doses

```{r refProfDoses,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
mbin<-data.frame(xat=sort(unique(dataRef$time)))
mbin$grp<-grmat$grp[match(mbin$xat,grmat$xat)]
mpref1<-pltab<-NULL
for(idose in sort(unique(dataRef$dose))) {
  msim<-matsim[matsim$dose==idose,]
  msim$grp<-grmat$grp[match(msim$time,grmat$xat)]
  colnames(msim)[4]<-"ysim"
  mpref<-aux.npdeplot.meanprof(mbin,msim)
  q1<-tapply(msim$ysim,msim$grp,quantile,c(0.025,0.5,0.975))
  gr1<-sort(unique(msim$grp))
  pltab1<-NULL
  for(i in 1:length(q1))
    pltab1<-rbind(pltab1,
                  c(gr1[i], q1[[i]]))
  colnames(pltab1)<-c("grp","lower","ymed","upper")
  pltab1<-data.frame(pltab1)
  pltab1<-pltab1[order(pltab1$grp),]
  pltab1<-cbind(xat=mbin$xat[match(pltab1$grp,mbin$grp)],pltab1, dose=idose)
  pltab<-rbind(pltab,pltab1)
  mpref$ymin<-mpref$mean-1.96*mpref$sd
  mpref$ymax<-mpref$mean+1.96*mpref$sd
  mpref$dose<-idose
  mpref1<-rbind(mpref1, mpref)
}
p1 <- ggplot(pltab,aes(x=xat,y=ymed)) + geom_ribbon(aes(x=xat, ymin=lower, ymax=upper), fill="lightblue",alpha=0.5) + geom_line(colour="blue") + geom_line(data=mpref1, aes(x=xat, y=mean),linetype="dashed", col="red", alpha=0.8) + geom_line(data=mpref1, aes(x=xat, y=ymin),linetype="dashed", col="red", alpha=0.8) + geom_line(data=mpref1, aes(x=xat, y=ymax),linetype="dashed", col="red", alpha=0.8) + facet_wrap(.~dose,ncol=3,scales="free")
print(p1)
```

### Reference profile for ages between 40 and 55

- poor reference profile in this case as too heterogenous (all doses)
- peak at time=3 because only dose=1000 for this timepoint so mean much higher

```{r refProfAges,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
mbin<-data.frame(xat=sort(unique(dataRef$time)))
mbin$grp<-grmat$grp[match(mbin$xat,grmat$xat)]
msim<-matsim[matsim$age >= 40 & matsim$age <= 55,]
msim$grp<-grmat$grp[match(msim$time,grmat$xat)]
colnames(msim)[4]<-"ysim"
mpref<-aux.npdeplot.meanprof(mbin,msim)
q1<-tapply(msim$ysim,msim$grp,quantile,c(0.025,0.5,0.975))
gr1<-sort(unique(msim$grp))
pltab<-NULL
for(i in 1:length(q1))
  pltab<-rbind(pltab,
               c(gr1[i], q1[[i]]))
colnames(pltab)<-c("grp","lower","ymed","upper")
pltab<-data.frame(pltab)
pltab<-pltab[order(pltab$grp),]
pltab<-cbind(xat=mbin$xat[match(pltab$grp,mbin$grp)],pltab)
mpref$ymin<-mpref$mean-1.96*mpref$sd
mpref$ymax<-mpref$mean+1.96*mpref$sd
p1 <- ggplot(pltab,aes(x=xat,y=ymed)) + geom_ribbon(aes(x=xat, ymin=lower, ymax=upper), fill="lightblue",alpha=0.5) + geom_line(colour="blue") + geom_line(data=mpref, aes(x=xat, y=mean),linetype="dashed", col="red", alpha=0.8) + geom_line(data=mpref, aes(x=xat, y=ymin),linetype="dashed", col="red", alpha=0.8) + geom_line(data=mpref, aes(x=xat, y=ymax),linetype="dashed", col="red", alpha=0.8)
print(p1)

table(msim$time, msim$dose)
```

## Scatterplots with reference plots

### Transformation for reference plots

Transforming obsmat and pimat:

- pimat
  - the PI are initially computed as the quantiles (eg 0.05, 0.5, 0.95 for a 90% PI) of the npde in npdesim (assuming they were computed from the observation matrix)
  - the reference profile had us compute the mean and SD of the observations, eg $E(f(\phi | \theta))$ and $SD(f(\phi | \theta))$
- obsmat
  - for npde: we have the values of the npde
    - transformation
      - $E(f(\phi | \theta))$ + npde$_{ij} \times SD(f(\phi | \theta))$ (?)
      - same transformation applied to the boundaries, medians of the PI and of the empirical percentiles
  - for npd same
- we observe the same outlier bands on the transformed npde profile as on the original npde
  - note: does not appear on corresponding VPC ? (for dose=1000) **check**

```{r transformPI,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# With simulated data
cat("First step: compute and check the mean profile for all possible time points\n")
mbin<-data.frame(xat=sort(unique(dataRef$time)))
mbin$grp<-grmat$grp[match(mbin$xat,grmat$xat)]
msim<-matsim[matsim$id==5,]
msim$grp<-grmat$grp[match(msim$time,grmat$xat)]
colnames(msim)[4]<-"ysim"
mpref<-aux.npdeplot.meanprof(mbin,msim)

q1<-tapply(msim$ysim,msim$grp,quantile,c(0.025,0.5,0.975))
gr1<-unique(msim$grp)
pltab<-NULL
for(i in 1:length(q1))
  pltab<-rbind(pltab,
               c(gr1[i], q1[[i]]))
colnames(pltab)<-c("grp","lower","ymed","upper")
pltab<-data.frame(pltab)
pltab<-cbind(xat=mbin$xat[match(pltab$grp,mbin$grp)],pltab)
mpref$ymin<-mpref$mean-1.96*mpref$sd
mpref$ymax<-mpref$mean+1.96*mpref$sd
p1 <- ggplot(pltab,aes(x=xat,y=ymed)) + geom_ribbon(aes(x=xat, ymin=lower, ymax=upper), fill="lightblue",alpha=0.5) + geom_line(colour="blue") + geom_line(data=mpref, aes(x=xat, y=mean),linetype="dashed", col="red", alpha=0.8) + geom_line(data=mpref, aes(x=xat, y=ymin),linetype="dashed", col="red", alpha=0.8) + geom_line(data=mpref, aes(x=xat, y=ymax),linetype="dashed", col="red", alpha=0.8)
print(p1)
cat("We should see close agreement between the ribbon and the lines from the reference profile.\n")

#  Transforming observations
cat("Second step: transform observations as tnpde_ij = E(t_ij) + SD(t_ij)* npde_ij \n")
# tobsmat$grp<-grmat$grp[match(tobsmat$time,grmat$xat)]
npdesim$tnpde<-mpref$mean[npdesim$grp] + mpref$sd[npdesim$grp]*npdesim$npde
cat("Should superimpose approximately to the reference profile")
p1 + geom_point(data=npdesim,aes(x=time, y=tnpde), colour="steelblue4", alpha=0.7, size=0.8)
tobsmat<-npdesim[,c(5,2)]
tobsmat$y<-npdesim$tnpde
colnames(tobsmat)<-c("grp","x","y")
tobsmat$category<-"none"
tobsmat$cens<-0
tobsmat$loq<-0

# Computing prediction intervals
cat("Third step: compute PI using aux.npdeplot.computepi (done above)\n")
print(head(pimat))

# Transforming prediction intervals
cat("Fourth step: transform PI\n")
for(icol in 4:15) {
  pimat[,icol]<-mpref$mean[pimat$grp] + mpref$sd[pimat$grp]*pimat[,icol]
}

# Creating obsmat for aux.npdeplot.plot
cat("Fifth step: plot\n")
plot.opt$which<-"tnpde"
aux.npdeplot.plot.eco(tobsmat, pimat, plot.opt)
cat("Works, PI for dose=1000 are much larger for VPC than npde when they should be relatively similar + the profile seems to have a different shape => to investigate\n")

if(createDat) {
  saveRDS(tobsmat,file.path(notesDir,"obsmat_tnpde_ecopk.rds"))
  saveRDS(pimat,file.path(notesDir,"pimat_tnpde_ecopk.rds"))
}


# Same, with npd (using the same pimat)
npdesim$tnpd<-mpref$mean[npdesim$grp] + mpref$sd[npdesim$grp]*npdesim$npd
tobsmat2<-tobsmat
tobsmat2$y<-npdesim$tnpd
plot.opt$which<-"tnpd"
aux.npdeplot.plot.eco(tobsmat2, pimat, plot.opt)

# Log-plot
plot.opt$which<-"tnpde"
plot.opt$ylog <- TRUE
aux.npdeplot.plot.eco(tobsmat, pimat, plot.opt)
plot.opt$ylog <- FALSE
# Changing names
if(FALSE ){
  colnames(pimat3)[1]<-"xbin"
  colnames(pimat3)[5:16]<-c("pinf.lower","pmid.lower","psup.lower","pinf.median", "pmid.median", "psup.median","pinf.upper","pmid.upper","psup.upper","obs.inf","obs.median","obs.sup")
  pimat3<-pimat3[,1:16]
  plot.opt2$which<-"tnpde"
  aux.npdeplot.plot.eco(obsmat3, pimat3, plot.opt2)
}
```


