---
title: "Code merge - Scatterplots"
author: "Emmanuelle Comets"
date: "26/01/2021"
output:
  pdf_document: default
  html_document: default
---

## Summary

### Objective

Check scatterplots produced by **npde.plot.scatter** and auxiilary functions.

### Current issues

- sorting the covariates in the facet plot
- labels on axes, titles
- box.plot: the width of the boxplots doesn't seem right (much thicker at the beginning but the groups should be equal size)

### Requirements

- main function  **npde.plot.scatterplot()**
  - input: npdeObject, which.x, which.y (X and Y variables to plot), ref.prof (refrence profile), "..."
  - output: one plot
- auxiliary functions **aux.npdeplot.scatter()** 
  - input:
    - a dataframe obs.mat: matrix of Y observations to plot (Y= yobs, npde, npd, pd, tnpde, tnpd) versus X (X=independent variable (eg time), predictions (pred), covariates (cov)), with the following columns
      - x,y: values of X and Y
      - grp: grouping factor - used to sort groups if plot.box=TRUE
      - cens: 1 if censored, 0 otherwise
      - loq: value of LOQ for the observation (used in VPC plot to optionally plot the line y=LOQ)
      - category: value of the category ("all" or "none" if not split by a covariate)
    -  pi.mat: matrix of PI and empirical percentiles to plot for each bin, with columns
      - grp: grouping factor (same as obs.mat) - not used
      - xcent: X-value used as center of each bin (one value of xcent per grp)
      - category: covariate category ("all" if over all)
      - 3 prediction intervals: pinf, pmid, psup (mid=middle, inf, sup= extreme PIs)
        - for each PI, 3 quantiles: lower, median, upper (ie usually 0.025, 0.5, 0.975)
        - for each PI, the empirical percentile for the observed data: obs.inf, obs.median, obs.sup
      - plot.opt: a list of graphical options used in the plot
  - output
    - distribution plots: histogram (aux.plot.hist), ecdf or qqplot (aux.plot.dist)
    - note: QQ-plot for uniform variable is similar to ecdf (theoretical quantiles correspond to the cumulative density function)

### Defining folders, loading libraries

```{r setup, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(grid)
library(mclust)
library(testthat)
#workDir<-"D:/RECHERCHES/_NPDE/Npde-2021/npde30-main"
workDir<-"/home/eco/work/npde/npde30"
notesDir<-file.path(workDir,"notebooks")
datDir<-file.path(workDir,"npde","data")
testsDir<-file.path(workDir,"npde","tests","testthat")
setwd(workDir)
```

### Loading functions

```{r setupOldPackage, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Classes from the package
source(file.path(workDir,"npde","R","aaa_generics.R"))
source(file.path(workDir,"npde","R","npdeControl.R"))
source(file.path(workDir,"npde","R","NpdeData.R"))
source(file.path(workDir,"npde","R","NpdeSimData.R"))
source(file.path(workDir,"npde","R","NpdeData-methods.R"))
source(file.path(workDir,"npde","R","NpdeRes.R"))
source(file.path(workDir,"npde","R","NpdeRes-methods.R"))
source(file.path(workDir,"npde","R","NpdeObject.R"))
source(file.path(workDir,"npde","R","NpdeObject-methods.R"))

# Computational functions from the package
source(file.path(workDir,"npde","R","compute_distribution.R"))
source(file.path(workDir,"npde","R","compute_npde.R"))
source(file.path(workDir,"npde","R","compute_pd.R"))
source(file.path(workDir,"npde","R","compute_ploq.R"))
source(file.path(workDir,"npde","R","mainNpde.R"))
source(file.path(workDir,"npde","R","npde.R"))

# Plot functions from the package - kept, some changes
source(file.path(workDir,"npde","R","plotNpde-methods.R"))
source(file.path(workDir,"npde","R","plotNpde-plotFunctions.R"))
source(file.path(workDir,"npde","R","plotNpde-binningPI.R")) # renamed from plotNpde-unitFunctionsPI.R

# Scatterplots
source(file.path(workDir,"npde","R","plotNpde-auxScatter.R")) # replaces plotNpde-unitFunctionsRef.R
source(file.path(workDir,"npde","R","plotNpde-auxScatterPlot.R"))
source(file.path(workDir,"npde","R","plotNpde-scatterplot.R")) # replaces plotNpde-meanProf.R
source(file.path(workDir,"npde","R","plotNpde-covplot.R"))

# Distribution plots
source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
source(file.path(workDir,"npde","R","plotNpde-distributionPlot.R")) # extracted "main" for distribution plots from plotNpde-plotFunctions.R

```

### Run npde

```{r runNpde, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Warfarin data, using files on disk
wbase<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(datDir, "simwarfarinBase.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

wcov<-autonpde(namobs=file.path(datDir, "warfarin.tab"),namsim=file.path(datDir, "simwarfarinCov.tab"), iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))
```

### Prepare obsmat for npde/pd versus x, with or without covariates sex and weight

```{r prepareObsmat, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
npdeObject<-wbase
plot.opt<-npdeObject["prefs"]
###################
# Binning on x
xbin<-npde.binning(wbase@data@data$time, wbase@prefs, verbose=FALSE)
matbin<-data.frame(grp=1:length(xbin$xcent), xcent=xbin$xcent, binlabel = names(xbin$xcent))

###################
# no covariate
obs.nocov<-data.frame(x=wbase@data@data$time, y=wbase@results@res[,"npde"], grp=xbin$xgrp)
obs.nocov$cens<-0
obs.nocov$category<-factor("all")

###################
# Covariate sex
obs.sex<-obs.nocov
obs.sex$category<-paste("sex:", wbase@data@data$sex)
obs.sex$category <- factor(obs.sex$category)

###################
## covariate weight
obs.weight<-data.frame(x=wbase@data@data$time, y=wbase@results@res[,"npde"], grp=xbin$xgrp)
obs.weight$cens<-0

idobs <- wbase@data@data$id
zecov<-wbase@data@data$wt
lcov<-"Weight"
ucov = zecov[match(unique(idobs),idobs)]
if(is.numeric(ucov) & length(unique(ucov))>plot.opt$ncat){ # Continuous covariatewith more than plot.opt$ncat (default 3)
  if(plot.opt$ncat!=3) { # 3 categories or less
    ncat<-plot.opt$ncat
    seqcat<-seq(0,1,length.out=(ncat+1))
    zecov.cat<-cut(zecov,breaks=quantile(ucov,seqcat), include.lowest=TRUE, ordered_result=TRUE)
    nam1<-paste("q",format(seqcat[-(ncat+1)],digits=2),"-q",format(seqcat[-1],digits=2),sep="")
    namcat<-paste(namcov,nam1,sep=": ")
    zecov.cat<-factor(zecov.cat, labels=namcat)
  } else { # if more than 3 categories, split in 3 ranges
    zecov.cat<-cut(zecov,breaks=quantile(ucov,c(0,0.25,0.75,1)), include.lowest=TRUE, ordered_result=TRUE)
    namcat<-paste(lcov,c("<Q1","Q1-Q3",">Q3"),sep=": ")
    zecov.cat<-factor(zecov.cat, labels=namcat)
  }
} else { # Categorical covariate defined as factor, or covariate with less than plot.opt$ncat categories
  namcat<-paste(lcov,unique(ucov), sep=": ")
  zecov.cat<-paste(lcov, zecov, sep=": ")
  zecov.cat<-factor(zecov.cat, labels=namcat)
}
obs.weight$category<-zecov.cat

# with pd
obspd.sex<-obs.sex
obspd.sex$y<-wbase@results@res[,"pd"]


###################
# Covariate weight as x, not yet binned
obsxcov.weight<-obs.weight
obsxcov.weight$category<-"all"
obsxcov.weight$x<-wbase@data@data$wt

###################
# Quantiles of weight as x
obsxcov.weight2<-obs.weight
obsxcov.weight2$x<-match(obs.weight$category, namcat)
obsxcov.weight2$category<-"all"
obsxcov.weight2$grp<-obsxcov.weight2$x

###################
# Covariate sex as x, not yet binned
obsxcov.sex<-obs.sex
obsxcov.sex$x<-wbase@data@data$sex
obsxcov.sex$grp<-as.integer(obsxcov.sex$x==1)+1
obsxcov.sex$x<-as.integer(obsxcov.sex$x==1)+1

obsxcov.sex$category<-"all"

obsxcov.sex2<-obs.sex
obsxcov.sex2$category<-"all"
obsxcov.sex2$x<-factor(wbase@data@data$sex, levels=c(0,1), labels=c("Male", "Female"))
```

### Prepare pimat for npde/pd versus x, with or without covariates sex and weight

```{r preparePImat, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# One pimat is no covariate
pimat.nocov<-aux.npdeplot.pimat(obs.nocov, xcent=matbin$xcent, distrib="norm", approx.pi=TRUE, sim.ypl=NULL)

# Covariate sex
obsmat<-obs.sex
pimat<-NULL
for(icat in levels(obsmat$category)) {
  obsmat.cov<-obsmat[obsmat$category==icat,]
  pimat.cov<-aux.npdeplot.pimat(obsmat.cov, xcent=matbin$xcent, distrib="norm", approx.pi=TRUE, sim.ypl=NULL)
  pimat<-rbind(pimat,pimat.cov)
}
pimat.sex<-pimat

# Covariate weight
obsmat<-obs.weight
pimat<-NULL
for(icat in levels(obsmat$category)) {
  obsmat.cov<-obsmat[obsmat$category==icat,]
  pimat.cov<-aux.npdeplot.pimat(obsmat.cov, xcent=matbin$xcent, distrib="norm", approx.pi=TRUE, sim.ypl=NULL)
  pimat<-rbind(pimat,pimat.cov)
}
pimat.weight<-pimat

# Covariate sex, y=pd
obsmat<-obspd.sex
pimat<-NULL
for(icat in levels(obsmat$category)) {
  obsmat.cov<-obsmat[obsmat$category==icat,]
  pimat.cov<-aux.npdeplot.pimat(obsmat.cov, xcent=matbin$xcent, distrib="unif", approx.pi=TRUE, sim.ypl=NULL)
  pimat<-rbind(pimat,pimat.cov)
}
pimat.pdsex<-pimat
```

### Plots for npde/pd versus cov, for covariates sex and weight

- 2 versions for continuous covariate
  - with PI for weight, computed as if x=time
  - without PI for weight, weight in 3 categories
- for categorical covariate
  - remove bands and interpolation ?
  - boxplot for categorical covariate

```{r preparePImatCov, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
# Scatterplot npde vs weight
head(obsxcov.weight)
binweight<-npde.binning(obsxcov.weight$x, plot.opt)
obsxcov.weight$grp<-binweight$xgrp
pimatxcov.weight<-aux.npdeplot.pimat(obsxcov.weight, xcent=binweight$xcent, distrib="norm", approx.pi=TRUE, sim.ypl=NULL)
plot.opt2<-plot.opt
plot.opt2$covsplit<-FALSE
plot.opt2$xlab<-"Weight (kg)"
plot.opt2$ylab<-"npde"
aux.npdeplot.scatter(obsxcov.weight,pimatxcov.weight, plot.opt2)

# Version with boxplots for weight
pimatxcov.weight2<-aux.npdeplot.pimat(obsxcov.weight2, xcent=sort(unique(obsxcov.weight2$x)), distrib="norm", approx.pi=TRUE, sim.ypl=NULL)

aux.npdeplot.boxcov(obsxcov.weight2,pimatxcov.weight2, plot.opt2)


# Scatterplot npde vs sex
head(obsxcov.sex)
pimatxcov.sex<-aux.npdeplot.pimat(obsxcov.sex, xcent=c(1,2), distrib="norm", approx.pi=TRUE, sim.ypl=NULL)
plot.opt2<-plot.opt
plot.opt2$covsplit<-FALSE
plot.opt2$xlab<-"Sex"
plot.opt2$ylab<-"npde"
aux.npdeplot.scatter(obsxcov.sex,pimatxcov.sex, plot.opt2)

# Version with boxplots for sex
aux.npdeplot.boxcov(obsxcov.sex,pimatxcov.sex, plot.opt2)

ggplot(obsxcov.sex, aes(x=x, y=y, group=factor(grp, ordered=TRUE))) + geom_boxplot(varwidth = TRUE)+ 
  geom_point(data = pimatxcov.sex, aes(x = grp, y = pmid.median), color=plot.opt$col.med) 

#
obs1<-obsxcov.sex
pim1<-pimatxcov.sex
obs1$grp<-factor(obs1$grp, labels=c("Sex:0", "Sex:1"))
aux.npdeplot.boxcov(obs1,pimatxcov.sex, plot.opt2)
pim1$grp<-factor(pim1$grp, labels=c("Sex:0", "Sex:1"))

ggplot(obs1, aes(x=grp, y=y, group=grp)) + geom_boxplot(varwidth = TRUE)+ 
  geom_point(data = pim1, aes(x = grp, y = pmid.median), color=plot.opt$col.med) 

```


## Debug functions

### Debug auxiliary plots

```{r auxScatterPlot}
plot.opt2<-plot.opt
aux.npdeplot.scatter(obs.nocov, pimat.nocov, plot.opt2)

plot.opt2<-plot.opt
plot.opt2$which.cov<-c("sex")
plot.opt2$covsplit<-TRUE
aux.npdeplot.scatter(obs.sex, pimat.sex, plot.opt2)

plot.opt2<-plot.opt
plot.opt2$which.cov<-c("wt")
plot.opt2$covsplit<-TRUE
aux.npdeplot.scatter(obs.weight, pimat.weight, plot.opt2)

plot.opt2<-plot.opt
plot.opt2$which.cov<-c("sex")
plot.opt2$covsplit<-TRUE
aux.npdeplot.scatter(obspd.sex, pimat.pdsex, plot.opt2)

# box plots
plot.opt2<-plot.opt
plot.opt2$plot.box<-TRUE
aux.npdeplot.scatter(obs.nocov, pimat.nocov, plot.opt2)

plot.opt2$which.cov<-c("sex")
plot.opt2$covsplit<-TRUE
aux.npdeplot.scatter(obspd.sex, pimat.pdsex, plot.opt2)

```

Covariate plots

```{r auxCovPlot}
# Boxplot versus weight
lcov<-"Wt"
obsxcov.weight2$grp<-factor(obsxcov.weight2$grp, labels=paste(lcov,c("<Q1","Q1-Q3",">Q3"),sep=": "))
pimatxcov.weight2$grp<-factor(pimatxcov.weight2$grp,labels=paste(lcov,c("<Q1","Q1-Q3",">Q3"),sep=": "))
plot.opt2<-plot.opt
plot.opt2$covsplit<-FALSE
plot.opt2$xlab<-"Weight (kg)"
plot.opt2$ylab<-"npde"
aux.npdeplot.boxcov(obsxcov.weight2,pimatxcov.weight2, plot.opt2)

# Boxplot versus sex
obsxcov.sex$grp<-factor(obsxcov.sex$grp, labels=c("Sex:0", "Sex:1"))
pimatxcov.sex$grp<-factor(pimatxcov.sex$grp, labels=c("Sex:0", "Sex:1"))
plot.opt2<-plot.opt
plot.opt2$xlab<-"Sex"
plot.opt2$ylab<-"npde"
aux.npdeplot.boxcov(obsxcov.sex,pimatxcov.sex, plot.opt2)

if(FALSE) {
  obsmat<-obsxcov.sex
  pimat<-pimatxcov.sex
}

# Same, with observations (not sure that makes sense)
obsycov.weight<-obsxcov.weight2
obsycov.weight$y<-wbase@data@data$dv
pimatycov.weight<-aux.npdeplot.pimat(obsycov.weight, xcent=sort(unique(obsxcov.weight$x)), distrib="norm", approx.pi=FALSE, sim.ypl=wbase@sim.data@datsim$ysim)

plot.opt2<-plot.opt
plot.opt2$xlab<-"Weight (kg)"
plot.opt2$ylab<-"y"

aux.npdeplot.boxcov(obsycov.weight,pimatycov.weight, plot.opt2)

```

### Debug main scatterplot function

```{r mainScatterPlot}
source(file.path(workDir,"npde","R","plotNpde-scatterplot.R")) # renamed from plotNpde-unitFunctionsAux.R
npde.plot.scatterplot(wbase,  which.x="x", which.y="npde")

# Split by covariate
npde.plot.scatterplot(wbase,  which.x="x", which.y="npde", covsplit=TRUE, which.cov=c("wt"))
npde.plot.scatterplot(wbase,  which.x="x", which.y="npde", covsplit=TRUE, which.cov=c("sex"))
npde.plot.scatterplot(wbase,  which.x="x", which.y="npde", covsplit=TRUE, which.cov=c("all"))

# PD vs time
npde.plot.scatterplot(wbase,  which.x="x", which.y="pd")

# Reference profile
npde.plot.scatterplot(wbase,  which.x="x", which.y="npde", ref.prof=list(id=1))

# VPC
npde.plot.scatterplot(wbase,  which.x="x", which.y="yobs")

npde.plot.scatterplot(wbase,  which.x="x", which.y="yobs", covsplit=TRUE)

npde.plot.scatterplot(wbase,  which.x="x", which.y="yobs", plot.box=TRUE)

# Scatterplot versus covariates
npde.plot.scatterplot(wbase,  which.x="cov", which.y="npde", which.cov=c("wt","sex"))

# Treating sex as factor
wbase@data@data$sex<-factor(wbase@data@data$sex)
npde.plot.scatterplot(wbase,  which.x="cov", which.y="npde", which.cov=c("sex"))

if(FALSE) {
  npdeObject<-wbase
  which.x<-"cov"
  which.y<-"npde"
  plot.opt<-npdeObject@prefs
  ref.prof<-NULL
}

```

### Debug boxplot of npde versus covariates (Brendel et al. 2010)

```{r mainCovPlot}
source(file.path(workDir,"npde","R","plotNpde-covplot.R"))

npde.plot.covariate(wbase, which.y="npde", which.cov="sex")
npde.plot.covariate(wbase, which.y="npde", which.cov=c("wt","sex"))
npde.plot.covariate(wbase, which.y="yobs", which.cov=c("wt","sex"), ylab="Warfarin concentrations (mg/L)")


if(FALSE) {
  npdeObject<-wbase
  which.y<-"npde"
  plot.opt<-npdeObject@prefs
}
```

