---
title: "Testing package with devtools"
author: "Emmanuelle Comets"
date: "02/02/2021"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

## Notes before release

- package
  -  **TODO** automatically load libraries when loading *npde* ()
    - ggplot2 not loaded, gridExtra, mclust not loaded
    - check: mclust
  - compilation: compiled package as npde 3.0
    - version number 3.0 because reference profiles included
    - lots of error messages for "no visible binding for global variable" in variables related to ggplot2 (Undefined global functions or variables) => hope this does not block us for CRAN
- TODO *npde website* (bookdown, Eco)
- code **TODO** for 3.1
  - add an option to remove all output when required and remove warnings if requested
- **TODO** simplify output for *show()* function (v3.0 or v3.1 ?)

## Setup, loading libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(ggplot2)
library(gridExtra)
library(mclust)
library(testthat)
library(grid)
workDir<-"D:/RECHERCHES/_NPDE/Npde-2021/npde30-main/"
setwd(workDir)
knitr::opts_chunk$set(root.dir = workDir)
#docFigs<-"/home/eco/work/npde/doclib/figs"
saveDocPlots<-FALSE
savePaperPlots<-FALSE
```

### Install package in development mode
  
```{r devModeInstall}
dev_mode() # development mode
install.packages(pkgs=file.path(workDir,"npde_3.0.tar.gz"),repos=NULL)
library(npde)

source(file.path(workDir,"npde","R","aaa_generics.R"))
source(file.path(workDir,"npde","R","npdeControl.R"))
source(file.path(workDir,"npde","R","NpdeData.R"))
source(file.path(workDir,"npde","R","NpdeSimData.R"))
source(file.path(workDir,"npde","R","NpdeData-methods.R"))
source(file.path(workDir,"npde","R","NpdeRes.R"))
source(file.path(workDir,"npde","R","NpdeRes-methods.R"))
source(file.path(workDir,"npde","R","NpdeObject.R"))
source(file.path(workDir,"npde","R","NpdeObject-methods.R"))

# Computational functions from the package
source(file.path(workDir,"npde","R","compute_distribution.R"))
source(file.path(workDir,"npde","R","compute_npde.R"))
source(file.path(workDir,"npde","R","compute_pd.R"))
source(file.path(workDir,"npde","R","compute_ploq.R"))
source(file.path(workDir,"npde","R","mainNpde.R"))
source(file.path(workDir,"npde","R","npde.R"))

# Plot functions from the package - kept, some changes
source(file.path(workDir,"npde","R","plotNpde-methods.R"))
source(file.path(workDir,"npde","R","plotNpde-plotFunctions.R"))
source(file.path(workDir,"npde","R","plotNpde-binningPI.R")) # renamed from plotNpde-unitFunctionsPI.R

# Distribution plots
source(file.path(workDir,"npde","R","plotNpde-auxDistPlot.R")) # renamed from plotNpde-unitFunctionsAux.R
source(file.path(workDir,"npde","R","plotNpde-distributionPlot.R")) # extracted "main" for distribution plots from plotNpde-plotFunctions.R

# Scatterplots
source(file.path(workDir,"npde","R","plotNpde-auxScatter.R")) # replaces plotNpde-unitFunctionsRef.R
source(file.path(workDir,"npde","R","plotNpde-auxScatterPlot.R"))
source(file.path(workDir,"npde","R","plotNpde-scatterplot.R")) # replaces plotNpde-meanProf.R


```

## Running examples from documentation

### Checking help files work

OK

```{r helpFiles, echo=FALSE}
?theopp
?autonpde
```
###  Computing npde for theophylline data

Checking that the results are the same when we use data frames versus files on disk: OK

Missing data (lines with MDV=1) removed from the data for plots (also removed from simulated data for approx.pi=TRUE, as per documentation the simulated and observed data must have compatible dimensions).

```{r theoRun, echo=FALSE}
data(theopp)
data(simtheopp)

# Calling autonpde with dataframes
theofit1<-autonpde(theopp,simtheopp,1,3,4,boolsave=FALSE, units=list(x="hr",y="mg/L"))
theofit1

# Calling autonpde with names of files to be read from disk
write.table(theopp,"theopp.tab",quote=FALSE,row.names=FALSE)
write.table(simtheopp,"simtheopp.tab",quote=FALSE,row.names=FALSE)
theofit<-autonpde(namobs="theopp.tab", namsim="simtheopp.tab", iid = 1,
            ix = 3, iy = 4, imdv=0, boolsave = FALSE, units=list(x="hr",y="mg/L"))
head(theofit["results"]["res"])
cat("Same results with data frame and with data on disk:",identical(theofit,theofit1),"\n")

# Debug
if(FALSE) {
  npdeObject<-theofit1
  npde.plot.scatterplot(theofit1)
  distrib<-"norm"
  which<-"npde"
  plot.opt<-theofit1@prefs
  npde.plot.dist(theofit1)
}

```

Show and print function :

- modified so that print(theofit) shows the results of gof.test applied to the object
- show displays the first 10 lines of the results dataframe
- **TODO** simplify output for *show()* function (v3.0 or v3.1 ?)

```{r theShow, echo=FALSE}
show(theofit)

print(theofit)
```

###  Computing npde for viral load data

- For censored viral load data (20 or 50 cp/mL), we compute the npde using the different methods implemented in the package. We expect:
  - NS for yvir1, yvir20, yvir50 (complete datasets, and censored datasets with imputed BQL)
  - significant for ppred method
  - NS for omit method because we also omit BQL data in the simulations (so OK)
  - NS for ipred method

```{r virloadRun, echo=FALSE}
#Viral load data
data(virload)
data(virload20)
data(virload50)
data(simvirload)

#Plotting the data
par(mfrow=c(1,2))
plot(Log_VL~Time,data=virload,xlab="Time (d)",ylab="Viral loads, base 10 log-scale (cp/mL)")
plot(Log_VL~Time,data=virload50,xlab="Time (d)",ylab="Viral loads, base 10 log-scale (cp/mL)")

# Calling autonpde with dataframes
yvir1<-autonpde(virload,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE, units=list(x="hr", y="cp/mL, log 10 base"))

yvir20<-autonpde(virload20,simvirload,iid=1,ix=2,iy=3, icens=4, boolsave=FALSE)

yvir2<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE)

yvir50<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE)

# Different methods to handle LOQ
yvir50.omit<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="omit")

yvir50.ppred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4,boolsave=FALSE, cens.method="ppred")

yvir50.ipred<-autonpde(virload50,simvirload,iid=1,ix=2,iy=3, icens=4, iipred=5, boolsave=FALSE, cens.method="ipred")

if(savePaperPlots) {
  paperFigs<-"/home/eco/xtex/npde/aaps20/figs"
  namfile<-file.path(paperFigs,"npdeDefault.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir1,bin.method="optimal")
  dev.off()  
}
```

```{r warfarinRun, include=FALSE,echo=FALSE,error=FALSE, warning=FALSE,message=FALSE}
data(warfarin)
data(simwarfarinBase)
data(simwarfarinCov)

wbase<-autonpde(namobs=warfarin,namsim=simwarfarinBase, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

#wcov<-autonpde(namobs=warfarin,namsim=simwarfarinCov, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfCov", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

wcov<-autonpde(namobs=warfarin,namsim=simwarfarinCov, iid=1,ix=2,iy=4,icov=c("amt" ,"wt" , "sex","age"),namsav="warfCov", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

# Warfarin with MDV
datDir<-file.path(workDir,"npde","data")
warfmdv<-read.table(file.path(datDir, "warfarin.tab"), header=TRUE)
idx<-sample(1:dim(warfmdv)[1], 10)
warfmdv$mdv<-0
warfmdv$mdv[idx]<-1
expect_equal(sum(warfmdv$mdv),10)

wmdv<-autonpde(namobs=warfmdv,namsim=file.path(datDir, "simwarfarinCov.tab"), iid=1,ix=2,iy=4,imdv=9,icov=c(3,6:8),namsav="warfBase", units=list(x="hr",y="ug/L", covariates=c("mg","kg","-","yr")))

```
## Test plots - default options
  
### Default plots for theophylline data

- **BUGS Romain TODOO**
  - **solved** title: in the waffle plot, only one title should appear, above all the 4 graphs (not one title per graph)
  - ajout de la condition plot.opt$plot.default==FALSE) pour l'affichage des titres dans les plot
  
  - **solved** no axes in the histogram plot => add
  
  - **solved** **X-range on PI** extend prediction band to min/max X (it seems to stop at the center of the bin) => option ???
  
- **Note** :dans plotNpde-auxScatterPlot: 1er bin avec valeur minimal de la borne et dernier bin avec valeur maximal de la borne. Les plots sur me 1er et dernier bin ne s'arrêtent pas au milieu du bin.
  
  - **global options** not passing on to the functions
    - **solved** size
      - **solved** normalement si l'utilisateur spécifie "size=2" sans spécifier size.pobs, size.pobs devrait passer à 1.5, et là ça ne semble rien changer
      - **solved** ni dans le graphe par défault (ie les 4 graphes), ni individuellement 
    - **solved** colours
      - **solved** when only col is specified, it should affect other elements (but not sure which we had decided), here only affects histogram and col.lobs for qqplot
      - **solved** col => col.pobs, col.lobs, col.pcens ?
      - **solved** col.lobs ne change rien, devrait changer les lignes correspondant aux percentiles et les lignes dans l'histograme
      
- **WARNING** attention aux effets de bord !!!
  - dans **set.plotoptions.NpdeObject**, xlab et ylab étaient fixés par défaut or on veut pouvoir les fixer automatiquement dans les fonctions graphiques tout en laissant l'utilisateur les passer en argument => on ne peut pas les mettre par défaut (xlab et ylab dépendent ici des variables qu'on veut tracer) => réfléchir avant de faire un truc comme ça (ou bien documenter qu'on puisse voir pourquoi ça plante, sinon on perd du temps à trouver pourqoui ça ne marche pas)
  
- **Note** : dans la dernière version, la fonction NpdeControl a toujours dans ses argumens xlab="" et ylab"" + which et xaxis
Dabs plotNpde-distributionPlot l.156-l.168 il y a différents tests qui restent en conséquence. Pour le moment ça n'empêche pas à l'utilisateur/utilisatrice de changer les labels à sa guise. 

```{r theoPlots, echo=FALSE}
# plot by default
plot(theofit1)
plot(theofit1, main="Theophylline data")
plot(theofit1, which="pd")
plot(theofit1, which="npd")
plot(theofit1, which="faux") # should throw an error => yes
plot(theofit1,size=5)
plot(theofit1,col="green",size=3)
plot(theofit1,col.pobs="green",size.pobs=3)
plot(theofit1,col.pobs="green",size.pobs=3,plot.type="x.scatter")
plot(theofit1,col.pobs="green",size.pobs=3,plot.type="x.scatter", ylab="ylab", xlab="xlab")
```

### Default plots for viral load data

- computation of the PI: seems appropriate in the different cases
- **Problems**  \textcolor{red}{(Eco)}
  - PI for omit aren't consistent with the VPC later on
    - **documentation** explain how PI are computed in the omit case

```{r virloadPlots, echo=FALSE}
plot(yvir1, main="Complete dataset") # complete data
plot(yvir50, main="Dataset censored 50 cp/mL") # imputing LOQ data using cdf (recommended)
plot(yvir50.omit, main="Censored 50, censoring=omit") # omitting LOQ data
plot(yvir50.ipred, main="Censored 50, censoring=ipred") # imputing to individual predictions
plot(yvir50.ppred, main="Censored 50, censoring=ppred") # imputing to population predictions
plot(yvir50, which="pd")

# Debug : solved
npde.plot.scatterplot(yvir50.omit)
npde.plot.dist(yvir50.omit)
  
npdeObject<-yvir50.omit
which<-"npde"
plot.opt<-yvir50.omit@prefs
  
#which.x<-"x"
#which.y<-which

```
## Plots with default options

### Scatterplots

- **Problems**  \textcolor{red}{(à résoudre Romain)}
  - **solved** ylab for scatterplot doesn't appear (but works in waffle plot, wtf ?)
  - **solved** **size** ne passe pas (devrait changer à la fois size.pobs et size.pcens)
    - **solved** même pb que dans le graphe par défault (ie les 4 graphes)
  - **solved** calling plot with plot.type="x.scatter" and which="pd" (eg) triggers the message "Option which.y= x.scatter not recognised" => debug call to intermediate functions with arguments in **plotNpde-methods.R** (dispatching arguments given in ...)
  - **solved** plot.box has a weird aspect with seemingly empty boxes for the first 2 bins ?
- **Check**
  - **solved** size of boxes when plot.box=TRUE

```{r theoPlotsScatter, echo=FALSE}
plot(yvir20, plot.type="x.scatter") 
plot(yvir20, plot.type="pred.scatter")

plot(theofit1, plot.type="x.scatter", which="pd")
plot(theofit1, plot.type="pred.scatter", which="pd")

plot(yvir20, plot.type="x.scatter", plot.box=TRUE)
plot(yvir20, plot.type="x.scatter", plot.box=TRUE,xlim=c(-20,200))

plot(theofit1, plot.type="x.scatter",size=5)
plot(yvir50, plot.type="x.scatter",size.pobs=5, size.pcens=3,pch.pcens=20)

```
### Distribution plots

- **Problems**  \textcolor{red}{(à résoudre Romain)}
  - **solved** pb with **size** (comme plus haut, size ne passe pas, size.pobs/size.pcens passent)
- **Problems**  \textcolor{red}{(à résoudre Eco)}
  - **axe title** for ecdf plot (should be: 'npde' on X-axis (/pd/npd) and 'Empirical distribution function' on Y-axis) [done, check it works]

```{r theoPlotsDist, echo=FALSE}
plot(theofit1, plot.type="hist",which="npde")
plot(theofit1, plot.type="qqplot",which="npde")
plot(theofit1, plot.type="ecdf",which="npde")

# Same plots for pd, OK
plot(theofit1, plot.type="hist", which="pd")
plot(theofit1, plot.type="qqplot", which="pd")
plot(theofit1, plot.type="ecdf", which="pd")

plot(yvir20, plot.type="qqplot", which="npde",size=5)
plot(yvir20, plot.type="qqplot", which="npde",size.pobs=5)

if(FALSE) { # ecdf of a uniform distribution (Eco check)
  x1<-runif(1000)
  plot(sort(x1),c(1:1000)/1000)
}
```
### Data plots

- **Problems**  \textcolor{red}{(à résoudre Romain)}

- **Note** pour cette version ça fait beaucoup à modifier, à commencer par plotNpde-methods puis npde.plot.data où le slot data est à pre,dre ne compte dans le reste du code. 
  - plot d'un **objet npdeData** ne marche pas
    - par contre plot.type="data" de l'objet npdeObject fonctionne => bizarre, vérifier [normalement plot.type="data" devrait appeler plot(objet@data) mais là ça semble court-circuiter ceci => à rectifier, on veut plutôt l'inverse]
    - problem with the data in the presence of **LOQ data**, the data being plotted is the LOQ
    - if applied directly to an objet npdeData (eg *plot(yivr50@data)*) => should plot y or the LOQ (ie censoring value)
    - if applied to the **npdeObject** resulting from a run => data plotted should depend on the censoring method (same as VPC)
      - for cdf, plot imputed y
      - for omit, don't plot anything
      - for ipred, plot ipred
      - for ppred, plot ppred
    - all other options should be the same [axis titles, axes, grid, default colours, etc...]
    
  - **solved** **lines for axes** don't appear
  - **solved** **size** 
    - size should be controlled by size.pobs and size.pcens, currently too small (not the same defaults as for the other plots ?)
    - size doesn't change size.pobs and size.lobs as it should
    - size.lobs doesn't work
    
- **Note** 
  - entre l.obs, p.obs, etc. qui modifie qui au final ? L'utilisation de templates ggplot serait-elle plus appropriée ? On utilise directement la syntaxe ggplot + on modifie les paramètres directement dans les listes *theme()* et *layers()*. Il y aurait ainsi les templates par défauts + les templates utilisateurs.
  
  - **solved** **axis titles**
    - missing for theofit, why ? (present for yvir50, so odd)
    
  - **solved** **line.loq** doesn't work (no line appears at the LOQ)

```{r theoPlotsData, echo=FALSE}
#Plotting the theophylline data (R vanilla)
plot(Conc~Time,data=theopp,xlab="Time after dose (hr)",ylab="Theophylline concentration (mg/L)")

cat("Failed test, no output\n")
plot(theofit1@data) # ne marche pas

plot(theofit1, plot.type="data",size.pobs=5)

plot(yvir50, plot.type="data",size.pobs=5)

plot(yvir50.omit, plot.type="data") 
plot(yvir50, plot.type="data",plot.loq=TRUE)
plot(yvir50, plot.type="data",plot.loq=TRUE, line.loq=TRUE)
plot(yvir50, plot.type="data",plot.loq=FALSE, line.loq=TRUE)

plot(yvir50,plot.type="data",size=5) 
plot(yvir50,plot.type="data",size.pobs=5, size.pcens=1.5) # pas sûr avec pcens + loq
plot(yvir50,plot.type="data",lwd.lobs=1.5) 

```
### VPC

- **Problems**  \textcolor{red}{(à résoudre Romain)}
  - **Y-axis**  missing
  - problem with the PI not being interpolated properly (??? thought that worked :-/ )

- **Notes to check Eco**
  - computation of the PI for **omit** consistent with the PI computed for npde ?
    - compute the PI in this case by omitting the data>LOQ for the simulated data as well, to be consistent with the way the PI are computed for npde
    - check also that the PI are computed consistently for ppred
    - ipred ??? in this case can't be consistent (we have isim in the dataset but not ipred) so keep the simulations as is
  - **but** VPC with LOQ data done as here => \textcolor{red}{Eco TODO:} expliquer dans la doc les méthodes de censoring et la différence entre les graphes npde et VPC dans le cas de la méthode omit (message=the discrepancy seen in VPC comes from not treating observed and simulated data in the same way, "corrected" in npde but at the price of a loss of power)

```{r theoPlotsVPC, echo=FALSE}
plot(theofit1, plot.type="vpc")
plot(yvir50.omit, plot.type="vpc", main="Viral load, method=omit") # correct except Y-axis title
plot(yvir50, plot.type="vpc", main="Viral load, method=cdf") 
plot(yvir50.ipred, plot.type="vpc", main="Viral load, method=ipred")
plot(yvir50.ppred, plot.type="vpc", main="Viral load, method=ppred")

# avec les boxplot dont le paramètre with a été ajusté pour overlapper les bornes min et max de x-axis
plot(yvir20, plot.type="vpc", plot.box=TRUE)

```
## P(Y<LOQ)

-  **Problems**  \textcolor{red}{(à résoudre Romain)}
  - **solved** fails 
  -  avant, vérifier:
    - **solved** **PI** on ne voit pas les bornes extérieures du PI (ça devrait être contrôlé par lty.bands et col.bands aussi)
    - **solved** **axes** missing lines for axes
    - **solved** **lwd.bands** should probably be increased for this plot :-/ (compared to the others), but never mind => show an example in Beautiful graphs

```{r virPlotsPloq, echo=FALSE}
plot(yvir20, plot.type="loq")
plot(yvir20, plot.type="loq", lwd.bands=1.75)
```
## Covariate plots

## Covariates

### Splitting plots according to covariates

- **Problems**  \textcolor{red}{(à résoudre Romain)}
  - **solved** yes here we really need to extend PI to cover the whole X-range for x.scatter and pred.scatter (not VPC)
    - just the PI (not the observed percentiles or outlier bands)
  - **covsplit**
    - **solved** doesn't work with the default plots => behaviour TBD
      - with one covariate, gives default plot (not split by the covariate)
      - with several covariates, message *arrangeGrob(...) ...: nrow * ncol >= n is not TRUE
      - we should get default plots for each category of the covariate but maybe only for one covariate ??? (too crowded otherwise)
- **Problems**  \textcolor{red}{(à résoudre Eco)}
  - ordering categorical variable (?)
  - why is there a blank space in the pred.scatter plot for sex=1 ?
- **other checks to do**
  - check if PI extend on the X-range when less homogenous data

```{r warfCov, echo=FALSE}
plot(wcov, plot.type="x.scatter") 

# Working
plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov=c("sex"))
plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov=c("wt"))
plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov=c("sex","wt"))

plot(wcov, plot.type="pred.scatter", covsplit=TRUE, which.cov=c("sex","wt"))

plot(wcov, plot.type="vpc", covsplit=TRUE, which.cov=c("sex","wt"))

plot(wcov, plot.type="x.scatter", covsplit=TRUE)

plot(wcov, plot.type="vpc", covsplit=TRUE, which.cov=c("sex","wt"),xlim=c(0,80))
plot(wcov, plot.type="vpc",ylim=c(0,30),covsplit=TRUE, which.cov=c("wt"))

# graphe par défaut et waffle plot pour les données avec des covariables
plot(wcov, covsplit=TRUE, which.cov="sex")
plot(wcov, covsplit=TRUE, which.cov="sex",type.plot="default")
plot(wcov, covsplit=TRUE, which.cov=c("sex","wt"),type.plot="default")
plot(wcov, covsplit=TRUE, which.cov=c("sex","wt"))
plot(wcov, covsplit=FALSE, which.cov=c("sex","wt"))

plot(wcov, covsplit=TRUE, which.cov=c("sex","wt","amt","age"))

plot(wcov, covsplit=TRUE, which.cov=c("sex","wt","amt"),main=c("waffle plot : Sex","waffle plot : Wt", "waffle plot : amt"))
plot(wbase, covsplit=TRUE, which.cov=c("sex","wt","amt"),main=c("waffle plot : Sex","waffle plot : Wt", "waffle plot : amt"))
plot(wmdv,  covsplit=TRUE, which.cov=c("sex","wt","amt"),main=c("waffle plot : Sex","waffle plot : Wt", "waffle plot : amt"))

```

### Parameters versus covariates

- **Problems**  \textcolor{red}{(à résoudre Romain)}
  - **solved** yes here we really need to extend PI to cover the whole X-range for x.scatter and pred.scatter (not VPC)
    - **solved** just the PI (not the observed percentiles or outlier bands)
  - **solved** cov.scatter (eg npde versus covariates)
    - boxplot for categorical covariates (overlayed on PI)
    - here two different behaviours ?

```{r warfParvsCov, echo=FALSE}

plot(wcov, plot.type="cov.scatter", covsplit=TRUE)

plot(wcov, plot.type="cov.scatter", which.cov="wt")
plot(wcov, plot.type="cov.scatter", which.cov="wt", covsplit=TRUE)  

plot(wcov, plot.type="cov.scatter", which.cov="sex")
plot(wcov, plot.type="cov.scatter", which.cov="sex", covsplit=TRUE)  
```

## Creating the plots for the user guide

### Theophylline

- Default plots and VPC: **OK pour doc**
- **Not solved** **Problem** with plot of data (see above)  

```{r doc.theo, echo=FALSE}
if(saveDocPlots) {
# Raw data
  namfile<-file.path(docFigs,"xtheo_data_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(theofit1@data)
  dev.off()
# Diagnostics plots  
  namfile<-file.path(docFigs,"theophylline_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(theofit1)
  dev.off()
# VPC
  namfile<-file.path(docFigs,"theophylline_vpc_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(theofit1,plot.type="vpc")
  dev.off()
}
```
### Viral load data

- **TODO**
  - **solved** plot data
  - est-ce que les fonctions graphiques 'de base' pourraient renvoyer les graphes comme objet pour pouvoir ensuite en faire un *grid.arrange()* (on avait parlé de cette option pour pouvoir faire ensuite ses propres graphes comme avant) ?

- **Note**   - ok mais pour le moment que pour : hist, qqplot, x.scatter, pred.scatter, vpc, ecdf, data
  - le pipeline est le suivant : fonction auxliaire plot --> fonction plot --> plot dans plotNpde-methods

    - **solved** 2 graphes de données (voire 3)
    - **solved** 2 graphes de VPC côte à côte (=> donner code correspondant dans la doc)

```{r grid.arrange, echo=FALSE}

plot.x.scatter.yvir50 = plot(yvir50,plot.type="x.scatter")
plot.pred.scatter.yvir50 = plot(yvir50,plot.type="pred.scatter")
do.call(grid.arrange, c(plot.x.scatter.yvir50$npde, plot.pred.scatter.yvir50$npde, list( nrow=1, ncol=2)))

plot.vpc.yvir50 = plot(yvir50,plot.type="vpc")
plot.yvir50.omit = plot(yvir50.omit,plot.type="vpc")
do.call(grid.arrange, c(plot.vpc.yvir50, plot.yvir50.omit, list( nrow=1, ncol=2)))

```
- **Note**
- Pour modifier les graphes directement avec un template ggplot. Le theme dun plot ggplot est accessible via le slot theme et layers, exemple : *plot.vpc.yvir50$theme et plot.vpc.yvir50$layers*.On peut ainsi définir un template ggplot par defaut pour chaque plot et créer une fonction qui va directement le modifier en  fonctions des options utilisateurs. Comme *plot.vpc.yvir50$theme* et *plot.vpc.yvir50$layers* sont des listes, avec modifyList les slots sont facilement accessibles et modifiables. Dans les fonctions plots pourraient être ainsi appelées un theme tels que *theme_plot_vpc(), theme_plot_scatter(), etc.*

```{r doc.virload, echo=FALSE}

if(saveDocPlots) {
# Raw data
  namfile<-file.path(docFigs,"doc_data50_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir50@data, plot.loq=FALSE)
  plot(yvir50@data, impute.loq=FALSE)
  dev.off()
# Diagnostics plots, cdf method (default)
  namfile<-file.path(docFigs,"x50_cdf_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir50)
  dev.off()
# Diagnostics plots, omit method
  namfile<-file.path(docFigs,"x50_omit_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir50.omit)
  dev.off()
# Diagnostics plots, ipred method
  namfile<-file.path(docFigs,"x50_ipred_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir50.ipred)
  dev.off()
# Diagnostics plots, ppred method
  namfile<-file.path(docFigs,"x50_ppred_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir50.ppred)
  dev.off()
# VPC
  namfile<-file.path(docFigs,"doc_vpc50_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir50,plot.type="vpc")
  plot(yvir50.omit,plot.type="vpc")
  dev.off()
# P(Y<LOQ)
  namfile<-file.path(docFigs,"virload_ploq_gg.eps")
  cairo_ps(file = namfile, onefile = TRUE, fallback_resolution = 600, height=8.27, width=11.69)
  plot(yvir50,plot.type="loq", main=" ")
  dev.off()
}
```

## End of file, deactivating development mode

```{r deactivateDevMode, echo=FALSE, hide=T}
dev_mode()
```

