---
title: "Supplementary material AAPS J"
author: "Emmanuelle Comets"
date: "07/04/2021"
output:
  pdf_document: default
  html_document: default
---


## Loading libraries

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
# Libraries
library(gridExtra)
library(ggplot2)
library(grid)
library(devtools)
library(mclust)
```

### Install package in development mode

This is a snapshot of the version of npde released at the time of the revision of the paper submitted to AAPS Journal (version 3.1, April 2021). We use development mode to avoid messing up any existing installation of npde.

```{r devModeInstall}
dev_mode() # development mode
install.packages(pkgs="/home/eco/work/npde/npde30/npde_3.1.tar.gz",repos=NULL)
library(npde)
```

## Diagnostic plots for viral load example

### Default diagnostic plots for npd for the viral load example used in the paper

```{r virload, echo=FALSE}
#Viral load data
data(virload)
data(simvirload)

#Plotting the data
par(mfrow=c(1,2))
plot(Log_VL~Time,data=virload,xlab="Time (d)",ylab="Viral loads, base 10 log-scale (cp/mL)")

# Calling autonpde with dataframes
yvir<-autonpde(virload,simvirload,iid=1,ix=2,iy=3,boolsave=FALSE, units=list(x="h",y="cp/mL, log 10 base"))

plot(yvir)

# Saving figures to folder figsDir
figsDir<-getwd() #figsDir<-"/home/eco/xtex/npde/aaps20/figs"

if(FALSE) {
  namfile<-file.path(figsDir,paste("npdeDefault.","eps",sep=""))
  cairo_ps(file = namfile, width = 11, height = 8, pointsize=20)
  plot(yvir)
  dev.off()
}
```

### npd for the warfarin example in the documentation

Running the example:

```{r warfarin, echo=FALSE}
# Warfarin with covariate model
data(warfarin)
data(simwarfarinCov)
wcov<-autonpde(namobs=warfarin,namsim=simwarfarinCov, iid=1,ix=2,iy=4,icov=c(3,6:8),namsav="warfCov", units=list(x="h",y="mg/L", covariates=c("mg","kg","-","yr")))
```

Reference plot using all subjects (commented out: reference plot for subject 2)

```{r warfarinRefPlot, echo=FALSE}
plot.tnpde<-plot(wcov, plot.type="x.scatter", ref.prof="all", main="tnpd", ylim=c(0,20))
plot.vpc<-plot(wcov, plot.type="vpc", main="VPC", ylim=c(0,20))
grid.arrange(grobs=list(plot.tnpde, plot.vpc), nrow=1, ncol=2)

# Reference plot for subject 2 instead
# plot.tnpde<-plot(wcov, plot.type="x.scatter", ref.prof=list(id=2), main="tnpd with reference profile ID=2")


if(FALSE) {
  namfile<-file.path(figsDir,paste("referenceProfile.","eps",sep=""))
  cairo_ps(file = namfile, width = 11, height = 8, pointsize=20)
  grid.arrange(grobs=list(plot.tnpde, plot.vpc), nrow=1, ncol=2)
  dev.off()
}
```

The code below shows several diagnostic plots for covariates:

- plots of npd versus covariates
  - we can also plot the distribution of eg npd versus the categories as boxplots
- plots like scatterplots or distribution plots can be split over categories of covariates
  - we show this for weight (wt) and for sex

```{r warfarinCovPlot, echo=FALSE}
xwt.covscatt<-plot(wcov, plot.type="cov.scatter", which.cov="wt", bin.method="optimal")
xsex.scatt<-plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov="sex")

xsex.box<-plot(wcov, plot.type="covariates", which.cov="sex")
xsex.ecdf<-plot(wcov, plot.type="ecdf", covsplit=TRUE, which.cov="sex")

grid.arrange(grobs=list(xwt.covscatt,  xsex.box[[1]], xsex.scatt, xsex.ecdf), nrow=2, ncol=2)

# xwt.scatt<-plot(wcov, plot.type="x.scatter", covsplit=TRUE, which.cov="wt")
# xwt.qqplot<-plot(wcov, plot.type="qqplot", covsplit=TRUE, which.cov="wt")
# xwt.box<-plot(wcov, plot.type="covariates", which.cov="wt")
# xwt.npdvscov<-plot(wcov, plot.type="cov.scatter", which.cov="wt")
# # xsex.covscat<-npde.plot.scatterplot(wcov, which.x="cov", which.y="npd", which.cov="sex")
# xsex.qqplot<-plot(wcov, plot.type="qqplot", covsplit=TRUE, which.cov="sex")
# 
# # Sometimes object is returned as a list, if the message "only 'grobs' allowed in "gList"" appears then try using [[1]] after the object
# grid.arrange(grobs=list(xwt.scatt, xsex.scatt, xwt.qqplot, xsex.qqplot, xwt.box[[1]],  xsex.box[[1]]), nrow=3, ncol=2)

if(FALSE) {
  namfile<-file.path(figsDir,paste("covariateplots.","eps",sep=""))
  cairo_ps(file = namfile, width = 11, height = 8, pointsize=20)
#  grid.arrange(grobs=list(xwt.scatt, xsex.scatt, xwt.qqplot, xsex.qqplot, xwt.box[[1]],  xsex.box[[1]]), nrow=3, ncol=2)
  grid.arrange(grobs=list(xwt.covscatt,  xsex.box[[1]], xsex.scatt, xsex.ecdf), nrow=2, ncol=2)
  dev.off()
}

# grid.arrange(grobs=list(xwt.scatt, xwt.qqplot, xwt.box[[1]], xsex.scatt, xsex.qqplot, xsex.box[[1]]), nrow=2, ncol=3)
# grid.arrange(grobs=list(xwt.scatt, xwt.qqplot, xsex.scatt, xsex.qqplot), nrow=2, ncol=2)
```

## End of code
Exit development mode.

```{r devModeStop}
dev_mode() # development mode
```